### 2023-04-04 outputs/paper/paper.qmd
- Edited data cleaning - Drafted bar graphs and linear regression model on "paper.qmd" doc

---
title: "How Diverse is the MoMA: While Modern, Not Diverse in Its Artists and Directors"
subtitle: "An analysis of the MoMA's public datasets on their collections and exhibits"
author: Sakura Ariga
thanks: "Code and data are available at: https://github.com/sakura-ariga/MOMA_diversity_analysis.git."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

# Set up workspace 
library(tidyverse)
library(dplyr)
library(tidyr)
library(knitr)
library(kableExtra)
```

```{r}
#| echo: false

# Import cleaned data from the outputs folder, originally imported via the 02-data_cleaning.R file
cleaned_momaexhibit_data <- read.csv(here::here("outputs/data/cleaned_momaexhibit_data"))
cleaned_momadirectors_data <- read.csv(here::here("outputs/data/cleaned_momadirectors_data"))
cleaned_momaartists_data <- read.csv(here::here("outputs/data/cleaned_momaartists_data"))
cleaned_momaartworks_data <- read.csv(here::here("outputs/data/cleaned_momaartworks_data"))
```

# Introduction

# Data {#sec-data}
Investigating artists: 
```{r}
#| label: fig-artistnationality
#| fig-cap: Nationality Distribution of Consituents (Artists, Staff) in MoMA Exhibits
#| echo: false

# Bar graph showing nationality distribution of constituents MoMA exhibits
cleaned_momaexhibit_data |>
  ggplot(mapping = aes(x = Nationality)) +
  theme(axis.text.x = element_text(angle = 90, hjust=1)) +
  geom_bar(position = "dodge2")+
  labs(x = "Nationality", y = "Count of Constituents in MoMA Exhibits") 
```

```{r}
#| label: fig-artistgender
#| fig-cap: Gender Distribution of Consituents (Artists, Staff) in MoMA Exhibits
#| echo: false

# Bar graph showing gender distribution of constituents MoMA exhibits
cleaned_momaexhibit_data |> count(Gender) |>
  ggplot(mapping = aes(x = Gender, y = n)) +
  geom_col() + 
  theme(axis.text.x = element_text(angle = 90, hjust=1)) +
  labs(x = "Gender", y = "Count of Constituents in MoMA Exhibits") 
```

Investigating directors and department heads:
```{r}
#| label: fig-staffnationality
#| fig-cap: Nationality Distribution of Directors and Department Heads in MoMA
#| echo: false

# Bar graph showing nationality distribution of MoMA directors and department heads 
cleaned_momadirectors_data |>
  ggplot(mapping = aes(x = Nationality)) +
  theme(axis.text.x = element_text(angle = 90, hjust=1)) +
  geom_bar(position = "dodge2")+
  labs(x = "Nationality", y = "Count of MoMA Directors and Department Heads") 
```

```{r}
#| label: fig-staffgender
#| fig-cap: Gender Distribution of Directors and Department Heads in MoMA
#| echo: false

# Bar graph showing gender distribution of MoMA directors and department heads 
cleaned_momadirectors_data |>
  ggplot(mapping = aes(x = Gender)) +
  theme(axis.text.x = element_text(angle = 90, hjust=1)) +
  geom_bar(position = "dodge2")+
  labs(x = "Gender", y = "Count of MoMA Directors and Department Heads")
```

# Model

```{r}
#| label: fig-model
#| fig-cap: Linear regression model of 
#| echo: false

numeric_momadirectors_data <- 
  cleaned_momadirectors_data |>
  mutate(Gender = case_when(
    Gender == "Female" ~ 1,
    Gender == "Male" ~ 2,
  ))

gender_model <-
  lm(
    formula = Gender ~ DepartmentBeginYear,
    data = numeric_momadirectors_data
  )

summary(gender_model)
```

# Results

# Discussion
## First discussion point {#sec-first-point}

# References

### 2023-04-04 scripts/01-download_data.R

@@ -10,13 +10,25 @@
 library(tidyverse)
 
 #### Download data ####
-raw_momaexhibit_data <- read_csv("inputs/data/MoMAExhibitions1929to1989.csv")
-raw_momadirectors_data <- read_csv("inputs/data/MoMADirectorsDepartmentHeads.csv")
-raw_momaartists_data <- read_csv("inputs/data/MoMAArtists.csv")
-raw_momaartworks_data <- read_csv("inputs/data/MoMAArtworks.csv")
+raw_momaexhibit_data <- read_csv(
+  file = "https://raw.githubusercontent.com/MuseumofModernArt/exhibitions/master/MoMAExhibitions1929to1989.csv",
+  show_col_types = FALSE, 
+  skip = 0)
+raw_momadirectors_data <- read_csv(
+  file = "https://raw.githubusercontent.com/MuseumofModernArt/exhibitions/master/MoMADirectorsDepartmentHeads.csv",
+  show_col_types = FALSE,
+  skip = 0)
+raw_momaartists_data <- read_csv(
+  file = "https://media.githubusercontent.com/media/MuseumofModernArt/collection/master/Artists.csv",
+  show_col_types = FALSE,
+  skip = 0)
+#raw_momaartworks_data <- read_csv(
+#  file = "https://media.githubusercontent.com/media/MuseumofModernArt/collection/master/Artworks.csv",
+#  show_col_types = FALSE,
+#  skip = 0)
 
 #### Save data ####
 write_csv(raw_momaexhibit_data, "inputs/data/raw_momaexhibit_data") 
 write_csv(raw_momadirectors_data, "inputs/data/raw_momadirectors_data") 
 write_csv(raw_momaartists_data, "inputs/data/raw_momaartists_data") 
-write_csv(raw_momaartworks_data, "inputs/data/raw_momaartworks_data") 
+#write_csv(raw_momaartworks_data, "inputs/data/raw_momaartworks_data") 

### 2023-04-04 scripts/02-data_cleaning.R

@@ -53,6 +53,11 @@ cleaned_momaartists_data <-
   mutate(, 
          Age = EndDate - BeginDate)
 
+# Edit gender variable to remove duplicates and null from raw_momaexhibit_data
+test <- 
+  cleaned_momaexhibit_data |>
+  filter(Gender == "Female" | Gender == "Male"E)
+
 #### Save data ####
 write_csv(cleaned_momaexhibit_data, "outputs/data/cleaned_momaexhibit_data")
 write_csv(cleaned_momadirectors_data, "outputs/data/cleaned_momadirectors_data")

### 2023-04-05 outputs/paper/paper.qmd
- Updated README to indicate work in progress - Created a rough outline of the paper

@@
 date-format: "D MMMM YYYY"
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "The MoMA's public GitHub data on their exhibits and collections was analyzed to determine how diverse the artists and directors at the MoMA are.
+It was found that the MoMA is comprised largely of white men, but that this relationship has changed with time.
+This finding gives quantitative proof of the need for more representation within not jus the MoMA, but all American museums as a whole."
 format: pdf
@@
 # Introduction
+Diversity in museums is a topic that is increasingly being discussed and raised as a problem in museums.
+While the main goal of museums is to serve as cultural institutions and a place of learning, oftentimes the objects on display or the decision-making staff who work behind the scenes do not meet this mission of inclusion.
+
+This paper will investigate the level of diversity in one such museum: the Museum of Modern Art (also known as MoMA).
+Founded in 1929, the MoMA, as its name suggests, houses a collection of contemporary art pieces.
+It was originally created to go against traditional art museums by housing only modern art, and has since grown to become an influential cultural institution.
+Using data made publicly available on the MoMA's GitHub account, this paper aims to evaluate how diverse the artists of the artworks on display are, as well as how diverse the directors and department heads who chose to display these artworks are, in terms of gender and nationality.
+Thus, the estimand is: how much of the artists and directors in the MoMA's history are/were not white men.
+
+It was found that the MoMA's artists and directors were predominantly men. A simple linear regression model shows that time affects this proportion of men.
+
+The paper's structure begins by explaining the data used, followed by a linear model, a discussion of the relationship between variables in the data and in the model, and a discussion on key findings.
 

### 2023-04-06 outputs/paper/paper.qmd
Added discussion headers to outline of final paper

@@
 ```
-
+\newpage
 ```{r}
@@
 ```
-
+\newpage
 Investigating directors and department heads:
@@
 ```
-
+\newpage
 # Model
@@
 # Discussion
-## First discussion point {#sec-first-point}
+## Gender distribition {#sec-first-point}
+## Nationality distribition {#sec-second-point}
+## Analyzing the model: is time a factor? {#sec-third-point}
+## Comparing artists vs directors {#sec-fourth-point}
 

### 2023-04-18 outputs/paper/paper.qmd
- Created model drafts

--- 2023-04-05 outputs/paper/paper.qmd
@@
 library(kableExtra)
+library(rstanarm)
+library(modelsummary)
 ```
@@
 # Introduction
+
 Diversity in museums is a topic that is increasingly being discussed and raised as a problem in museums.
@@
 # Data {#sec-data}
+
 Investigating artists:
+
 ```{r}
@@
 ```
+
+\newpage
 
@@
 
+\newpage
+
 Investigating directors and department heads:
+
 ```{r}
@@
 
+\newpage
+
 ```{r}
@@
 
-gender_model <-
+potential_gender_model <-
   lm(
@@
 
-summary(gender_model)
+summary(potential_gender_model)
 ```
+
+The goal of our modelling strategy is twofold. Firstly,...
+
+Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+
+## Model set-up
+
+Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+
+\begin{align} 
+y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
+\mu_i &= \alpha + \beta_i + \gamma_i\\
+\alpha &\sim \mbox{Normal}(0, 2.5) \\
+\beta &\sim \mbox{Normal}(0, 2.5) \\
+\gamma &\sim \mbox{Normal}(0, 2.5) \\
+\sigma &\sim \mbox{Exponential}(1)
+\end{align}
+
+We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+
+### Model justification
+
+We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+
+We can use maths by including latex between dollar signs, for instance $\theta$.
 
@@
 
+Our results are summarized in @tbl-modelresults.
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+gender_model <-
+  readRDS(file = here::here("outputs/models/gender_model.rds"))
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-modelresults
+#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| warning: false
+modelsummary::modelsummary(
+  list(
+    "First model" = gender_model
+  ),
+  statistic = "mad",
+  fmt = 2
+)
+```
+
 # Discussion
-## First discussion point {#sec-first-point}
+
+## Gender distribition {#sec-first-point}
+
+## Nationality distribition {#sec-second-point}
+
+## Analyzing the model: is time a factor? {#sec-third-point}
+
+## Comparing artists vs directors {#sec-fourth-point}
+
+## Weaknesses and next steps
+
+\newpage
+
+\appendix
+
+# Appendix {-}
+
+# Additional data details
+
+# Model details {#sec-model-details}
+
+## Posterior predictive check
+
+In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
+
+In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-ppcheckandposteriorvsprior
+#| layout-ncol: 2
+#| fig-cap: "Examining how the model fits, and is affected by, the data"
+#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
+#pp_check(first_model) +
+#  theme_classic() +
+#  theme(legend.position = "bottom")
+#posterior_vs_prior(first_model) +
+#  theme_minimal() +
+#  scale_color_brewer(palette = "Set1") +
+#  theme(legend.position = "bottom") +
+#  coord_flip()
+```
+
+## Diagnostics
+
+@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
+
+@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-stanareyouokay
+#| fig-cap: "Checking the convergence of the MCMC algorithm"
+#| fig-subcap: ["Trace plot", "Rhat plot"]
+#| layout-ncol: 2
+#plot(first_model, "trace")
+#plot(first_model, "rhat")
+```
+
+\newpage
 

### 2023-04-18 scripts/00-simulate_data.R

@@ -1,11 +1,9 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Data: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Simulates the data that I would like to obtain from the MoMA's public GitHub for my analysis
+# Author: Sakura Ariga 
+# Data: 15 April 2023
+# Contact: sakura.ariga@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
 
 
 #### Workspace setup ####

### 2023-04-18 scripts/01-download_data.R

@@ -1,9 +1,9 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
+# Purpose: Downloads and saves the data from the MoMA's public GitHub
 # Author: Sakura Ariga
 # Date: 26 March 2023
 # Contact: sakura.ariga@mail.utoronto.ca 
-# License: MIT [...UPDATE THIS...]
+# License: MIT
 
 
 #### Workspace setup ####

### 2023-04-18 scripts/02-data_cleaning.R

@@ -1,9 +1,9 @@
 #### Preamble ####
-# Purpose: Cleans.... [...UPDATE THIS...]
+# Purpose: Cleans MoMA data originally downloaded from the MoMA's public GitHub
 # Author: Sakura Ariga
 # Data: 26 March 2023
 # Contact: sakura.ariga@mail.utoronto.ca
-# License: MIT [...UPDATE THIS...]
+# License: MIT 
 
 
 #### Workspace setup ####
@@ -13,7 +13,7 @@ library(tidyverse)
 raw_momaexhibit_data <- read_csv("inputs/data/MoMAExhibitions1929to1989.csv")
 raw_momadirectors_data <- read_csv("inputs/data/MoMADirectorsDepartmentHeads.csv")
 raw_momaartists_data <- read_csv("inputs/data/MoMAArtists.csv")
-raw_momaartworks_data <- read_csv("inputs/data/MoMAArtworks.csv")
+#raw_momaartworks_data <- read_csv("inputs/data/MoMAArtworks.csv")
 
 #### Clean data ####
 # Remove unneeded info in raw_momaexhibit_data
@@ -34,12 +34,12 @@ cleaned_momaartists_data <-
   raw_momaartists_data |> 
   select(DisplayName, ArtistBio, Nationality, Gender, BeginDate, EndDate)
 # Remove unneeded info in raw_momaartworks_data
-cleaned_momaartworks_data <- 
-  raw_momaartworks_data |> 
-  select(Title, Artist, ArtistBio, Nationality, BeginDate, EndDate, Date, Medium, Dimensions, 
-         CreditLine, Classification, Department, DateAcquired, `Circumference (cm)`,
-         `Depth (cm)`, `Diameter (cm)`, `Height (cm)`, `Length (cm)`, `Weight (kg)`, 
-         `Width (cm)`, `Seat Height (cm)`, `Duration (sec.)`)
+#cleaned_momaartworks_data <- 
+#  raw_momaartworks_data |> 
+#  select(Title, Artist, ArtistBio, Nationality, BeginDate, EndDate, Date, Medium, Dimensions, 
+#         CreditLine, Classification, Department, DateAcquired, `Circumference (cm)`,
+#         `Depth (cm)`, `Diameter (cm)`, `Height (cm)`, `Length (cm)`, `Weight (kg)`, 
+#         `Width (cm)`, `Seat Height (cm)`, `Duration (sec.)`)
 
 # Create age variables by subtracting start dates from end dates 
[…]

### 2023-04-18 scripts/04-test_data.R

@@ -1,11 +1,9 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Data: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests the simulated data found in file "00-simulate_data.R"
+# Author: Sakura Ariga
+# Data: 15 April 2023
+# Contact: sakura.ariga@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
 
 
 #### Workspace setup ####

### 2023-04-18 scripts/05-model_data.R

@@ -1,0 +1,144 @@
+#### Preamble ####
+# Purpose: Models... [...UPDATE THIS...]
+# Author: Sakura Ariga
+# Data: 26 March 2023
+# Contact: sakura.ariga@mail.utoronto.ca
+# License: MIT
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(rstanarm)
+
+#### Notes from last day of class ####
+use default priors in the bayesian model --> can take it directly from telling stories with data (see quercus post for apr 6)
+pretty much whats on his apr 6 quercus, just change the first line 
+
+in paper: display the model equation, explain model, model justification (use olaedos paper as template)
+for model justification part, talk about whether you expect a positive or negative relationship, then add a paragraph about each 
+model section should be around a page in your paper 
+
+results section in paper is where you read in the model that you created; also put a table summary of it here
+
+#### Example model from Rohan ####
+first_model <-
+  stan_glm(
+    formula = flying_time ~ length + width,
+    data = analysis_data,
+    family = gaussian(),
+    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_aux = exponential(rate = 1, autoscale = TRUE),
+    seed = 853
+  )
+
+#### Draft model ####
+numeric_momadirectors_data <- 
+  cleaned_momadirectors_data |>
+  mutate(Gender = case_when(
+    Gender == "Female" ~ 1,
+    Gender == "Male" ~ 2,
+  ))
+
+potential_model <-
+  stan_glm(
+    formula = Gender ~ DepartmentBeginYear + Gender,
+    data = numeric_momadirectors_data,
+    family = gaussian(),
+    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_aux = exponential(rate = 1, autoscale = TRUE),
+    seed = 853
+  )
+
+summary(potential_model)
+
+#### Potential model 1 ####
+potential_model_1 <- 
+  stan_glm(
+    formula = PositionAge ~ Gender + Nationality,
+    data = numeric_momadirectors_data,
+    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+  )
[…]

### 2023-04-18 scripts/03-draft.R
- Saved models to outputs folder - Deleted draft R script as no longer needed - Renamed scripts

@@ -1,65 +1,0 @@
-#### Workspace setup #### 
-library(tidyverse)
-library(dplyr)
-library(tidyr)
-library(knitr)
-library(kableExtra)
-
-
-#### Import data ####
-# Import cleaned data from the outputs folder, originally imported via the 02-data_cleaning.R file
-cleaned_momaexhibit_data <- read.csv(here::here("outputs/data/cleaned_momaexhibit_data"))
-cleaned_momadirectors_data <- read.csv(here::here("outputs/data/cleaned_momadirectors_data"))
-cleaned_momaartists_data <- read.csv(here::here("outputs/data/cleaned_momaartists_data"))
-cleaned_momaartworks_data <- read.csv(here::here("outputs/data/cleaned_momaartworks_data"))
-
-
-#### Visualize data (drafts) ####
-# Bar graph showing gender distribution of artists displayed in the MoMA
-cleaned_momaartists_data |>
-  ggplot(mapping = aes(x = Gender)) + 
-  geom_bar(position = "dodge2")+
-  labs(x = "Gender", y = "Count of Artists in the MoMA") 
-
-# Bar graph showing nationality distribution of artists displayed in the MoMA
-cleaned_momaartists_data |>
-  ggplot(mapping = aes(x = Nationality)) +
-  theme(axis.text.x = element_text(angle = 90, hjust=1)) +
-  geom_bar(position = "dodge2")+
-  labs(x = "Nationality", y = "Count of Artists in the MoMA") 
-
-## Bar graph showing age distribution of artworks displayed in the MoMA (TOO BIG DATASET, TAKES TOO LONG)
-#cleaned_momaartworks_data |>
-#  ggplot(mapping = aes(x = Date)) +
-#  theme(axis.text.x = element_text(angle = 90, hjust=1)) +
-#  geom_bar(position = "dodge2")+
-#  labs(x = "Date", y = "Count of Artworks in the MoMA") 
-
-# Bar graph showing nationality distribution of constituents MoMA exhibits
-cleaned_momaexhibit_data |>
-  ggplot(mapping = aes(x = Nationality)) +
-  theme(axis.text.x = element_text(angle = 90, hjust=1)) +
-  geom_bar(position = "dodge2")+
-  labs(x = "Nationality", y = "Count of Constituents in MoMA Exhibits") 
-
-# Bar graph showing gender distribution of constituents MoMA exhibits
-cleaned_momaexhibit_data |>
[…]

### 2023-04-18 scripts/04-model_data.R

@@ -1,0 +1,99 @@
+#### Preamble ####
+# Purpose: Created models for paper analysis 
+# Author: Sakura Ariga
+# Data: 26 March 2023
+# Contact: sakura.ariga@mail.utoronto.ca
+# License: MIT
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(rstanarm)
+
+#### Potential model 2.1 ####
+# Create dataset for model 
+for (i in 1929:2023) {
+  temp <- 
+    cleaned_momadirectors_data |> 
+    filter(PositionBeginYear <= i & PositionEndYear >= i) |> 
+    group_by(Gender) |> 
+    summarise(n = n()) |> 
+    mutate(PercentageMale = (n / sum(n)) * 100) |> 
+    filter(Gender == "Male") |>
+    select(PercentageMale) |> 
+    mutate(Year = i)
+  
+  if (i == 1929) {
+    directors_gender_percentage <- temp
+  } else {
+    directors_gender_percentage <- directors_gender_percentage |> 
+      rows_append(temp)
+  }
+}
+
+directors_gender_percentage <- 
+  directors_gender_percentage |> 
+  mutate(PercentageFemale = 100 - PercentageMale)
+
+# Create model from created dataset above
+model_directors_percentage_female <- 
+  lm(
+    formula = PercentageFemale ~ Year,
+    data = directors_gender_percentage
+  )
+
+summary(model_directors_percentage_female) 
+
+
+#### Potential model 2.2 ####
+# Create dataset for model 
+exhibits_gender_percentage <- 
+    cleaned_momaexhibit_data |> 
+    filter(ExhibitionRole == "Artist") |> 
+    group_by(ExhibitionTitle, Gender, Year) |> 
+    summarise(n = n()) |> 
+    group_by(ExhibitionTitle, Year) |> 
+    mutate(PercentageMale = (n / sum(n)) * 100) |> 
+    filter(Gender == "Male") |>
+    select(PercentageMale)
+
+exhibits_gender_percentage <- 
+  exhibits_gender_percentage |> 
+  mutate(PercentageFemale = 100 - PercentageMale)
+
+# Create model from created dataset above
+model_exhibits_percentage_female <- 
+  lm(
+    formula = PercentageFemale ~ Year,
+    data = exhibits_gender_percentage
+  )
+
+summary(model_exhibits_percentage_female) 
+
+#### Potential model 2.3 ####
+merged_gender_percentage <- 
[…]

### 2023-04-18 scripts/05-model_data.R

@@ -1,144 +1,0 @@
-#### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Sakura Ariga
-# Data: 26 March 2023
-# Contact: sakura.ariga@mail.utoronto.ca
-# License: MIT
-
-
-#### Workspace setup ####
-library(tidyverse)
-library(rstanarm)
-
-#### Notes from last day of class ####
-use default priors in the bayesian model --> can take it directly from telling stories with data (see quercus post for apr 6)
-pretty much whats on his apr 6 quercus, just change the first line 
-
-in paper: display the model equation, explain model, model justification (use olaedos paper as template)
-for model justification part, talk about whether you expect a positive or negative relationship, then add a paragraph about each 
-model section should be around a page in your paper 
-
-results section in paper is where you read in the model that you created; also put a table summary of it here
-
-#### Example model from Rohan ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
-
-#### Draft model ####
-numeric_momadirectors_data <- 
-  cleaned_momadirectors_data |>
-  mutate(Gender = case_when(
-    Gender == "Female" ~ 1,
-    Gender == "Male" ~ 2,
-  ))
-
-potential_model <-
-  stan_glm(
-    formula = Gender ~ DepartmentBeginYear + Gender,
-    data = numeric_momadirectors_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
-
-summary(potential_model)
-
-#### Potential model 1 ####
-potential_model_1 <- 
-  stan_glm(
-    formula = PositionAge ~ Gender + Nationality,
-    data = numeric_momadirectors_data,
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-  )
[…]

### 2023-04-18 outputs/paper/paper.qmd
- Started models section in paper - Removed MoMA artists dataset from analysis as it is unused

@@
 # Model
-
-```{r}
-#| label: fig-model
-#| fig-cap: Linear regression model of 
-#| echo: false
-
-numeric_momadirectors_data <- 
-  cleaned_momadirectors_data |>
-  mutate(Gender = case_when(
-    Gender == "Female" ~ 1,
-    Gender == "Male" ~ 2,
-  ))
-
-potential_gender_model <-
-  lm(
-    formula = Gender ~ DepartmentBeginYear,
-    data = numeric_momadirectors_data
-  )
-
-summary(potential_gender_model)
-```
-
 The goal of our modelling strategy is twofold. Firstly,...
@@
 ```{r}
+#| label: fig-model1
+#| fig-cap: Linear regression model of the effect of time on the percentage of female MoMA directors
 #| echo: false
@@
 #| message: false
-gender_model <-
-  readRDS(file = here::here("outputs/models/gender_model.rds"))
+
+model_directors_percentage_female <-
+  readRDS(file = here::here("outputs/models/model_directors_percentage_female.rds"))
 ```
-
 ```{r}
@@
 #| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| tbl-cap: "Explanatory model of percentage of female MoMA directors based on year"
 #| warning: false
+
 modelsummary::modelsummary(
   list(
-    "First model" = gender_model
+    "First model" = model_directors_percentage_female
   ),
-  statistic = "mad",
+  fmt = 2
+)
+```
+
+```{r}
+#| label: fig-model2
+#| fig-cap: Linear regression model of the effect of exhibit year on the percentage of female MoMA artists
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
+model_exhibits_percentage_female <-
+  readRDS(file = here::here("outputs/models/model_exhibits_percentage_female.rds"))
+```
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-modelresults
+#| tbl-cap: "Explanatory model of percentage of female MoMA artists based on exhibit year"
+#| warning: false
+
+modelsummary::modelsummary(
+  list(
+    "Second model" = model_exhibits_percentage_female
+  ),
+  fmt = 2
+)
+```
+
+```{r}
+#| label: fig-model3
+#| fig-cap: Linear regression model of the effect of time and percentage of female MoMA directors on the percentage of female MoMA artists selected for exhibits
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
+model_exhibits_on_directors <-
+  readRDS(file = here::here("outputs/models/model_exhibits_on_directors.rds"))
+```
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-modelresults
+#| tbl-cap: "Explanatory model of percentage of female MoMA artists based on exhibit year and percentage of female MoMA directors "
+#| warning: false
+
+modelsummary::modelsummary(
+  list(
+    "Third model" = model_exhibits_on_directors
+  ),
   fmt = 2
@@
 ## Weaknesses and next steps
+- a LOT of NAs in the exhibit dataset, especially regarding artist gender, so results are skewed bc of that 
+- binary understanding of gender that is exclusive
 

### 2023-04-18 scripts/00-simulate_data.R

@@ -8,10 +8,6 @@
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+
 
 #### Simulate data ####
-# [...ADD CODE HERE...]
-
-
-

### 2023-04-18 scripts/01-download_data.R

@@ -18,17 +18,7 @@ raw_momadirectors_data <- read_csv(
   file = "https://raw.githubusercontent.com/MuseumofModernArt/exhibitions/master/MoMADirectorsDepartmentHeads.csv",
   show_col_types = FALSE,
   skip = 0)
-raw_momaartists_data <- read_csv(
-  file = "https://media.githubusercontent.com/media/MuseumofModernArt/collection/master/Artists.csv",
-  show_col_types = FALSE,
-  skip = 0)
-#raw_momaartworks_data <- read_csv(
-#  file = "https://media.githubusercontent.com/media/MuseumofModernArt/collection/master/Artworks.csv",
-#  show_col_types = FALSE,
-#  skip = 0)
 
 #### Save data ####
 write_csv(raw_momaexhibit_data, "inputs/data/raw_momaexhibit_data") 
 write_csv(raw_momadirectors_data, "inputs/data/raw_momadirectors_data") 
-write_csv(raw_momaartists_data, "inputs/data/raw_momaartists_data") 
-#write_csv(raw_momaartworks_data, "inputs/data/raw_momaartworks_data") 

### 2023-04-18 scripts/02-clean_data.R

@@ -8,12 +8,11 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(stringr)
 
 #### Download data ####
 raw_momaexhibit_data <- read_csv("inputs/data/MoMAExhibitions1929to1989.csv")
 raw_momadirectors_data <- read_csv("inputs/data/MoMADirectorsDepartmentHeads.csv")
-raw_momaartists_data <- read_csv("inputs/data/MoMAArtists.csv")
-#raw_momaartworks_data <- read_csv("inputs/data/MoMAArtworks.csv")
 
 #### Clean data ####
 # Remove unneeded info in raw_momaexhibit_data
@@ -29,17 +28,6 @@ cleaned_momadirectors_data <-
   select(DepartmentFullName, DepartmentBeginYear, DepartmentEndYear, DisplayName, PositionNote, 
          PositionBeginYear, PositionEndYear, ConstituentType, AlphaSort, Nationality, 
          ConstituentBeginDate, ConstituentEndDate, ArtistBio, Gender)
-# Remove unneeded info in raw_momaartists_data
-cleaned_momaartists_data <- 
-  raw_momaartists_data |> 
-  select(DisplayName, ArtistBio, Nationality, Gender, BeginDate, EndDate)
-# Remove unneeded info in raw_momaartworks_data
-#cleaned_momaartworks_data <- 
-#  raw_momaartworks_data |> 
-#  select(Title, Artist, ArtistBio, Nationality, BeginDate, EndDate, Date, Medium, Dimensions, 
-#         CreditLine, Classification, Department, DateAcquired, `Circumference (cm)`,
-#         `Depth (cm)`, `Diameter (cm)`, `Height (cm)`, `Length (cm)`, `Weight (kg)`, 
-#         `Width (cm)`, `Seat Height (cm)`, `Duration (sec.)`)
 
 # Create age variables by subtracting start dates from end dates 
 cleaned_momadirectors_data <-
@@ -47,16 +35,11 @@ cleaned_momadirectors_data <-
   mutate(ConstituentAge = ConstituentEndDate - ConstituentBeginDate,
          PositionAge = PositionEndYear - PositionBeginYear, 
          DepartmentAge = DepartmentEndYear - DepartmentBeginYear)
-# Create age variables by subtracting start dates from end dates 
-cleaned_momaartists_data <-
-  cleaned_momaartists_data |>
-  mutate(Age = EndDate - BeginDate)
 
[…]

### 2023-04-18 scripts/03-test_data.R

@@ -8,6 +8,6 @@
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+
 
 #### Test data ####

### 2023-04-18 scripts/04-model_data.R

@@ -10,8 +10,8 @@
 library(tidyverse)
 library(rstanarm)
 
-#### Potential model 2.1 ####
-# Create dataset for model 
+#### Model 1 ####
+# Create new dataset for model 
 for (i in 1929:2023) {
   temp <- 
     cleaned_momadirectors_data |> 
@@ -45,7 +45,7 @@ model_directors_percentage_female <-
 summary(model_directors_percentage_female) 
 
 
-#### Potential model 2.2 ####
+#### Model 2 ####
 # Create dataset for model 
 exhibits_gender_percentage <- 
     cleaned_momaexhibit_data |> 
@@ -70,9 +70,16 @@ model_exhibits_percentage_female <-
 
 summary(model_exhibits_percentage_female) 
 
-#### Potential model 2.3 ####
+#### Model 3 ####
 merged_gender_percentage <- 
   left_join(exhibits_gender_percentage, directors_gender_percentage, by = "Year")
+
+# merged_gender_percentage <- 
+#   merged_gender_percentage |> 
+#   rename = ("PercentageMaleArtists" = "PercentageMale.x")
+#             "PercentageFemaleArtists" = "PercentageFemale.x",
+#             "PercentageMaleDirectors" = "PercentageMale.y",
+#             "PercentageFemaleDirectors" = "PercentageFemale.y")
 
 model_exhibits_on_directors <- 
   lm(
@@ -89,11 +96,11 @@ saveRDS(
 )
 
 saveRDS(
-  exhibits_gender_percentage, 
-  file = "outputs/models/exhibits_gender_percentage.rds"
+  model_exhibits_percentage_female, 
+  file = "outputs/models/model_exhibits_percentage_female.rds"
 )
 
 saveRDS(
-  merged_gender_percentage, 
-  file = "outputs/models/merged_gender_percentage.rds"
+  model_exhibits_on_directors, 
+  file = "outputs/models/model_exhibits_on_directors.rds"
 )

### 2023-04-18 outputs/paper/paper.qmd
Wrote sections about the data and the model in paper.qmd

@@
 library(tidyverse)
-library(dplyr)
 library(tidyr)
@@
 cleaned_momadirectors_data <- read.csv(here::here("outputs/data/cleaned_momadirectors_data"))
-cleaned_momaartists_data <- read.csv(here::here("outputs/data/cleaned_momaartists_data"))
-cleaned_momaartworks_data <- read.csv(here::here("outputs/data/cleaned_momaartworks_data"))
 ```
@@
 # Data {#sec-data}
+### Data Source
+In this report, the 25795 observations from the ____ and 65 observations from the _______ are used to investigate the level of diversity among MoMA decision-making directors and displayed artists.
+This data was obtained from the MoMA's publicly available GitHub, which has several public repositories containing data regarding the museum [@MoMAGithub].
+For this analysis, the MoMA GitHub repositories of ____ [@____] and ____ [@__] were used.
+
+This report was created using the R statistical programming language [@R].
+For the results and analysis of this report, all figures were created using the tidyverse package [@tidyverse].
+Additionally, the tables were created using the packages knitr [@knitr] and kableExtra [@kableExtra], and the graphs were created using the packages tidyr [@tidyr] and ggplot2 [@ggplot2].
+
+### Variables of Interest
+
+Our report selects 7 variables for analysis.
+We focus on 6 particular factors that we predicted affects the amount of Internet use: age, sex, race, number of children, marital status, and happiness.
+In this paper, we investigate the influence of these various factors on the total number of hours of weekly Internet usage.
+The packages tidyverse [@tidyverse], haven [@haven], and reshape2 [@reshape2] were used to clean the dataset by grouping or converting the questionnaire responses into categorical or textual answers.
+
+The variables, Number of Children and Weekly Internet Hours, are recorded as a numerical value.
+Weekly Internet Hours has a maximum value of 168, as there are only 168 hours in a week.
+Age is also recorded as a numerical value, but is cleaned to represent ages in groups of ten years.
+The other variables, Sex, Race, Marital Status, and Happiness Level, are all recorded as a textual option for respondents to choose from.
 
@@
 #| label: fig-artistnationality
-#| fig-cap: Nationality Distribution of Consituents (Artists, Staff) in MoMA Exhibits
+#| fig-cap: Nationality Distribution of Artists in MoMA Exhibits
 #| echo: false
 
-# Bar graph showing nationality distribution of constituents MoMA exhibits
+# Bar graph showing nationality distribution of Artists in MoMA exhibits
 cleaned_momaexhibit_data |>
+  filter(ExhibitionRole == "Artist") |>
   ggplot(mapping = aes(x = Nationality)) +
-  theme(axis.text.x = element_text(angle = 90, hjust=1)) +
+  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
   geom_bar(position = "dodge2")+
-  labs(x = "Nationality", y = "Count of Constituents in MoMA Exhibits") 
+  labs(x = "Nationality", y = "Count of Artists in MoMA Exhibits") 
 ```
@@
 #| label: fig-artistgender
-#| fig-cap: Gender Distribution of Consituents (Artists, Staff) in MoMA Exhibits
+#| fig-cap: Gender Distribution of Artists in MoMA Exhibits
 #| echo: false
 
-# Bar graph showing gender distribution of constituents MoMA exhibits
-cleaned_momaexhibit_data |> count(Gender) |>
+# Bar graph showing gender distribution of Artists in MoMA exhibits
+cleaned_momaexhibit_data |> 
+  filter(ExhibitionRole == "Artist") |>
+  count(Gender) |>
   ggplot(mapping = aes(x = Gender, y = n)) +
@@
   theme(axis.text.x = element_text(angle = 90, hjust=1)) +
-  labs(x = "Gender", y = "Count of Constituents in MoMA Exhibits") 
+  labs(x = "Gender", y = "Count of Artists in MoMA Exhibits") 
 ```
@@
 # Model
-The goal of our modelling strategy is twofold. Firstly,...
+From the exploratory data analysis above, it is clear that both the number of female MoMA directors and the number of female artists displayed in the MoMA is much less than the number of male counterparts in these positions.
+This gender relationship is worth further investigation using linear models.
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+The goal of this modelling strategy is threefold.
+Firstly, the relationship between the percentage of female directors at the MoMA and years will be investigated to determine whether the gender distribution of those who have the highest decision-making power at the MoMA has improved over time.
+Secondly, another model will look at the relationship between the percentage of female artists in exhibits at the MoMA and years to determine whether the gender distribution of the artists displayed in MoMA exhibits has improved over time.
+Finally, the third model will investigate the effect that female director percentage in the MoMA has on female artist percentage in MoMA exhibits to determine whether the gender distribution of top MoMA decision-makers has an effect on the gender distribution of artists selected for exhibits.
 
-## Model set-up
+Here we briefly describe the three linear regression models used to investigate this relationship between gender and time.
+Background details and diagnostics are included in [Appendix -@sec-model-details].
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+## Model Set-Up
+The first linear regression model regarding the effect of time on the percentage of female MoMA directors is as follows:
+$$\hat{y} = \beta_0 + \beta_1x_{year}$$
 
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
+The output of this linear regression model gives the percentage of female MoMA directors.
+Thus, the response in the model is the percentage of female MoMA directors based on the year explanatory variable.
+A linear regression model was used because both the response variable and the explanatory variable are quantitative.
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+This model focuses on the following two aspects of MoMA directors:
+
+* Percentage of female MoMA directors, the response variable, is used as a quantitative measure of gender diversity that is between 0 and 100
+
+* Year, the explanatory variable, is a numeric variable between 1929 (the founding year of the MoMA) and 2023 (the year that this report was published) indicating a specific year in the history of the MoMA
+
+The second linear regression model regarding the effect of time on the percentage of female MoMA artists in the exhibits is similar to the first and is as follows:
+$$\hat{y} = \beta_0 + \beta_1x_{year}$$
+
+The output of this linear regression model gives the percentage of female MoMA artists whose works have been displayed in MoMA exhibits over time.
+Thus, the response in the model is the percentage of female MoMA artists based on the year explanatory variable.
+A linear regression model was used because both the response variable and the explanatory variable are quantitative.
+
+This model focuses on the following two aspects of MoMA artists:
+
+* Percentage of female MoMA artists, the response variable, is used as a quantitative measure of gender diversity that is between 0 and 100
+
+* Year, the explanatory variable, is a numeric variable between 1929 (the founding year of the MoMA) and 1990 (the year that the MoMA public GitHub has data until) indicating a specific year in the history of the MoMA
+
+The third and final linear regression model differs slightly from the previous two and is as follows:
+$$\hat{y} = \beta_0 + \beta_1x_{femaledirectorpercentage} + \beta_2x_{year}$$
+
+The output of this linear regression model gives the percentage of female MoMA artists whose works have been displayed in MoMA exhibits over time.
+Thus, the response in the model is the percentage of female MoMA artists based on the percentage of female MoMA directors and  year explanatory variables.
+A linear regression model was used because both the response variable and the explanatory variables are quantitative.
+
+This model focuses on the following three aspects of MoMA artists:
+
+* Percentage of female MoMA artists, the response variable, is used as a quantitative measure of gender diversity that is between 0 and 100
+
+* Percentage of female MoMA directors, an explanatory variable, is a numeric variable between 0 and 100 indicating the gender distribution of the directors who had the decision-making power to choose the artists to be displayed
+
+* Year, an explanatory variable, is a numeric variable between 1929 (the founding year of the MoMA) and 2023 (the year that this report was published) indicating a specific year in the history of the MoMA
+
+All of the models are run in R [@citeR] using the `stats` package of @stats.
 
@@
 ```
+
 ```{r}
@@
 #| eval: true
-#| label: tbl-modelresults
+#| label: tbl-modelresults1
 #| tbl-cap: "Explanatory model of percentage of female MoMA directors based on year"
@@
 #| eval: true
-#| label: tbl-modelresults
+#| label: tbl-modelresults2
 #| tbl-cap: "Explanatory model of percentage of female MoMA artists based on exhibit year"
@@
 #| eval: true
-#| label: tbl-modelresults
+#| label: tbl-modelresults3
 #| tbl-cap: "Explanatory model of percentage of female MoMA artists based on exhibit year and percentage of female MoMA directors "
@@
 ## Weaknesses and next steps
+
 -   a LOT of NAs in the exhibit dataset, especially regarding artist gender, so results are skewed bc of that
@@
 
-# Appendix {-}
+# Appendix {.unnumbered}
 

### 2023-04-18 scripts/02-clean_data.R

@@ -15,47 +15,47 @@ raw_momaexhibit_data <- read_csv("inputs/data/MoMAExhibitions1929to1989.csv")
 raw_momadirectors_data <- read_csv("inputs/data/MoMADirectorsDepartmentHeads.csv")
 
 #### Clean data ####
-# Remove unneeded info in raw_momaexhibit_data
+# Remove unneeded info in Exhibit data
 cleaned_momaexhibit_data <- 
   raw_momaexhibit_data |> 
   select(ExhibitionTitle, ExhibitionBeginDate, ExhibitionEndDate, ExhibitionRole, 
          ExhibitionRoleinPressRelease, ConstituentType, DisplayName, AlphaSort, 
          Institution, Nationality, ConstituentBeginDate, ConstituentEndDate, ArtistBio,
          Gender)
-# Remove unneeded info in raw_momadirectors_data
+# Remove unneeded info in Directors data
 cleaned_momadirectors_data <- 
   raw_momadirectors_data |> 
   select(DepartmentFullName, DepartmentBeginYear, DepartmentEndYear, DisplayName, PositionNote, 
          PositionBeginYear, PositionEndYear, ConstituentType, AlphaSort, Nationality, 
          ConstituentBeginDate, ConstituentEndDate, ArtistBio, Gender)
 
-# Create age variables by subtracting start dates from end dates 
+# Create age variables in Directors data by subtracting start dates from end dates 
 cleaned_momadirectors_data <-
   cleaned_momadirectors_data |>
   mutate(ConstituentAge = ConstituentEndDate - ConstituentBeginDate,
          PositionAge = PositionEndYear - PositionBeginYear, 
          DepartmentAge = DepartmentEndYear - DepartmentBeginYear)
 
-# Remove NAs from PositionEndYear
+# Remove NAs from PositionEndYear in Directors data
 cleaned_momadirectors_data$PositionEndYear[is.na(cleaned_momadirectors_data$PositionEndYear)] <- 2023
 
-# Create year variables for exhibit start and end 
+# Create year-specific variables for start and end dates in Exhibit data
 cleaned_momaexhibit_data <-
   cleaned_momaexhibit_data |>
   mutate(StartYear = str_sub(ExhibitionBeginDate, -4),
          Year = str_sub(ExhibitionEndDate, -4)
   )
 
-# Remove NAs from Year
+# Remove NAs from Year in Exhibit data
[…]

### 2023-04-18 scripts/04-model_data.R

@@ -10,6 +10,7 @@
 library(tidyverse)
 library(rstanarm)
 
+
 #### Model 1 ####
 # Create new dataset for model 
 for (i in 1929:2023) {
@@ -70,6 +71,7 @@ model_exhibits_percentage_female <-
 
 summary(model_exhibits_percentage_female) 
 
+
 #### Model 3 ####
 merged_gender_percentage <- 
   left_join(exhibits_gender_percentage, directors_gender_percentage, by = "Year")
@@ -88,6 +90,7 @@ model_exhibits_on_directors <-
   )
 
 summary(model_exhibits_on_directors)
+
 
 #### Save models ####
 saveRDS(

### 2023-04-19 scripts/02-clean_data.R
Removed unused variables from cleaned datasets

@@ -19,15 +19,15 @@ raw_momadirectors_data <- read_csv("inputs/data/MoMADirectorsDepartmentHeads.csv
 cleaned_momaexhibit_data <- 
   raw_momaexhibit_data |> 
   select(ExhibitionTitle, ExhibitionBeginDate, ExhibitionEndDate, ExhibitionRole, 
-         ExhibitionRoleinPressRelease, ConstituentType, DisplayName, AlphaSort, 
-         Institution, Nationality, ConstituentBeginDate, ConstituentEndDate, ArtistBio,
+         ConstituentType, DisplayName, 
+         Institution, Nationality, ConstituentBeginDate, ConstituentEndDate,
          Gender)
 # Remove unneeded info in Directors data
 cleaned_momadirectors_data <- 
   raw_momadirectors_data |> 
   select(DepartmentFullName, DepartmentBeginYear, DepartmentEndYear, DisplayName, PositionNote, 
-         PositionBeginYear, PositionEndYear, ConstituentType, AlphaSort, Nationality, 
-         ConstituentBeginDate, ConstituentEndDate, ArtistBio, Gender)
+         PositionBeginYear, PositionEndYear, Nationality, 
+         ConstituentBeginDate, ConstituentEndDate, Gender)
 
 # Create age variables in Directors data by subtracting start dates from end dates 
 cleaned_momadirectors_data <-

### 2023-04-19 scripts/02-clean_data.R
Further removed unused variables so that datasets only include variables used in the paper analysis

@@ -19,22 +19,12 @@ raw_momadirectors_data <- read_csv("inputs/data/MoMADirectorsDepartmentHeads.csv
 cleaned_momaexhibit_data <- 
   raw_momaexhibit_data |> 
   select(ExhibitionTitle, ExhibitionBeginDate, ExhibitionEndDate, ExhibitionRole, 
-         ConstituentType, DisplayName, 
-         Institution, Nationality, ConstituentBeginDate, ConstituentEndDate,
-         Gender)
+         DisplayName, Nationality, Gender)
 # Remove unneeded info in Directors data
 cleaned_momadirectors_data <- 
   raw_momadirectors_data |> 
-  select(DepartmentFullName, DepartmentBeginYear, DepartmentEndYear, DisplayName, PositionNote, 
-         PositionBeginYear, PositionEndYear, Nationality, 
-         ConstituentBeginDate, ConstituentEndDate, Gender)
-
-# Create age variables in Directors data by subtracting start dates from end dates 
-cleaned_momadirectors_data <-
-  cleaned_momadirectors_data |>
-  mutate(ConstituentAge = ConstituentEndDate - ConstituentBeginDate,
-         PositionAge = PositionEndYear - PositionBeginYear, 
-         DepartmentAge = DepartmentEndYear - DepartmentBeginYear)
+  select(DepartmentFullName, DisplayName, PositionBeginYear, PositionEndYear, 
+         Nationality, Gender)
 
 # Remove NAs from PositionEndYear in Directors data
 cleaned_momadirectors_data$PositionEndYear[is.na(cleaned_momadirectors_data$PositionEndYear)] <- 2023
@@ -46,13 +36,15 @@ cleaned_momaexhibit_data <-
          Year = str_sub(ExhibitionEndDate, -4)
   )
 
-# Remove NAs from Year in Exhibit data
-cleaned_momaexhibit_data$Year[is.na(cleaned_momaexhibit_data$Year)] <- 2023
-
 # Convert Year from string to numeric in Exhibit
 cleaned_momaexhibit_data <-
   cleaned_momaexhibit_data |>
   mutate(Year = as.numeric(Year))
+
+# Remove unneeded info in Exhibit data
+cleaned_momaexhibit_data <- 
+  cleaned_momaexhibit_data |> 
+  select(ExhibitionTitle, ExhibitionRole, DisplayName, Nationality, Gender, StartYear, Year)
          
 
 # Edit gender variable to remove duplicates and null from Exhibit

### 2023-04-19 scripts/02-clean_data.R
Further refined data to remove unused variables

@@ -18,8 +18,9 @@ raw_momadirectors_data <- read_csv("inputs/data/MoMADirectorsDepartmentHeads.csv
 # Remove unneeded info in Exhibit data
 cleaned_momaexhibit_data <- 
   raw_momaexhibit_data |> 
-  select(ExhibitionTitle, ExhibitionBeginDate, ExhibitionEndDate, ExhibitionRole, 
-         DisplayName, Nationality, Gender)
+  filter(ExhibitionRole == "Artist") |> 
+  select(ExhibitionTitle, ExhibitionBeginDate, ExhibitionEndDate, DisplayName, 
+         Nationality, Gender)
 # Remove unneeded info in Directors data
 cleaned_momadirectors_data <- 
   raw_momadirectors_data |> 
@@ -44,7 +45,7 @@ cleaned_momaexhibit_data <-
 # Remove unneeded info in Exhibit data
 cleaned_momaexhibit_data <- 
   cleaned_momaexhibit_data |> 
-  select(ExhibitionTitle, ExhibitionRole, DisplayName, Nationality, Gender, StartYear, Year)
+  select(ExhibitionTitle, DisplayName, Nationality, Gender, StartYear, Year)
          
 
 # Edit gender variable to remove duplicates and null from Exhibit

### 2023-04-19 scripts/00-simulate_data.R
Simulated data

@@ -11,3 +11,45 @@ library(tidyverse)
 
 
 #### Simulate data ####
+set.seed(853)
+
+artists_simulated_data <-
+  tibble(
+    year = c(1929:2023),
+    percentage_female = runif(
+      n = 95, 
+      min = 0, 
+      max = 100),
+    race = sample(
+      x = c(1:7),
+      size = 95,
+      replace = TRUE),
+    position = sample(
+      x = c("Artist"),
+      size = 95,
+      replace = TRUE)
+ )
+head(artists_simulated_data)
+
+directors_simulated_data <-
+  tibble(
+    year = c(1929:2023),
+    percentage_female = runif(
+      n = 95, 
+      min = 0, 
+      max = 100),
+    race = sample(
+      x = c(1:7),
+      size = 95,
+      replace = TRUE),
+    position = sample(
+      x = c("Director or Department Head"),
+      size = 95,
+      replace = TRUE)
+  )
+head(directors_simulated_data)
+
+
+#### Save simulated data ####
+write_csv(artists_simulated_data, "outputs/data/artists_simulated_data.csv")
+write_csv(directors_simulated_data, "outputs/data/directors_simulated_data.csv")

### 2023-04-19 scripts/04-model_data.R
Edited models based on modification of cleaned dataset

@@ -50,7 +50,6 @@ summary(model_directors_percentage_female)
 # Create dataset for model 
 exhibits_gender_percentage <- 
     cleaned_momaexhibit_data |> 
-    filter(ExhibitionRole == "Artist") |> 
     group_by(ExhibitionTitle, Gender, Year) |> 
     summarise(n = n()) |> 
     group_by(ExhibitionTitle, Year) |> 

### 2023-04-19 scripts/03-test_data.R
Created tests for simulated data

@@ -10,4 +10,26 @@
 library(tidyverse)
 
 
+#### Download data ####
+artists_simulated_data <- read_csv("outputs/data/artists_simulated_data.csv")
+directors_simulated_data <- read_csv("outputs/data/directors_simulated_data.csv")
+
+
 #### Test data ####
+artists_simulated_data$percentage_female |> 
+  class() == "numeric"
+
+artists_simulated_data$year |> 
+  class() == "numeric"
+
+artists_simulated_data$year |> 
+  min() == 1929
+
+directors_simulated_data$year |> 
+  max() == 2023
+
+directors_simulated_data$percentage_female |> 
+  min() >= 0
+
+directors_simulated_data$percentage_female |> 
+  max() <= 100

### 2023-04-19 scripts/02-clean_data.R
Changed to reproducible way of calling raw data

@@ -11,15 +11,15 @@ library(tidyverse)
 library(stringr)
 
 #### Download data ####
-raw_momaexhibit_data <- read_csv("inputs/data/MoMAExhibitions1929to1989.csv")
-raw_momadirectors_data <- read_csv("inputs/data/MoMADirectorsDepartmentHeads.csv")
+raw_momaexhibit_data <- read_csv("inputs/data/raw_momaexhibit_data")
+raw_momadirectors_data <- read_csv("inputs/data/raw_momadirectors_data")
 
 #### Clean data ####
 # Remove unneeded info in Exhibit data
 cleaned_momaexhibit_data <- 
   raw_momaexhibit_data |> 
   filter(ExhibitionRole == "Artist") |> 
-  select(ExhibitionTitle, ExhibitionBeginDate, ExhibitionEndDate, DisplayName, 
+  select(ExhibitionTitle, ExhibitionRole, ExhibitionBeginDate, ExhibitionEndDate, DisplayName, 
          Nationality, Gender)
 # Remove unneeded info in Directors data
 cleaned_momadirectors_data <- 

### 2023-04-19 outputs/paper/paper.qmd
- Added to draft of paper.qmd - Added to references.bib based on additional content in paper.qmd

@@
 library(kableExtra)
-library(rstanarm)
 library(modelsummary)
@@
 
-Diversity in museums is a topic that is increasingly being discussed and raised as a problem in museums.
+Diversity in cultural institutions is a topic that is increasingly being discussed and raised as a problem to be tackled, in museums in particular [@museumnext].
 While the main goal of museums is to serve as cultural institutions and a place of learning, oftentimes the objects on display or the decision-making staff who work behind the scenes do not meet this mission of inclusion.
@@
 Founded in 1929, the MoMA, as its name suggests, houses a collection of contemporary art pieces.
-It was originally created to go against traditional art museums by housing only modern art, and has since grown to become an influential cultural institution.
+It was originally created to go against traditional art museums by housing only modern art, and has since grown to become an influential cultural institution [@MoMA].
 Using data made publicly available on the MoMA's GitHub account, this paper aims to evaluate how diverse the artists of the artworks on display are, as well as how diverse the directors and department heads who chose to display these artworks are, in terms of gender and nationality.
-Thus, the estimand is: how much of the artists and directors in the MoMA's history are/were not white men.
+Thus, the estimand is: the percentage of artists, directors, and department heads in the MoMA's history who are / were not white men.
 
-It was found that the MoMA's artists and directors were predominantly men. A simple linear regression model shows that time affects this proportion of men.
+It was found that the MoMA's artists and directors were predominantly men.
+Simple linear regression models show that time affects this percentage of female artists, directors, and department heads in that the number of female artists has increased on average by ___ percentage points per year, while the number of female directors and department heads has increased on average by 0.25 percentage points per year.
+These findings are important because they provide numerical proof of the lack of gender diversity in the MoMA, both in the artists displayed and in the directors and department heads who choose the artists to display, which could motivate the MoMA to take active steps to better the gender representation within their institution.
 
-The paper's structure begins by explaining the data used, followed by a linear model, a discussion of the relationship between variables in the data and in the model, and a discussion on key findings.
+This paper's structure will begin by explaining the MoMA's publicly made available data regarding its artists and staff that is the subject of analysis.
+It will then explore this data to understand overall trends in nationality and gender distribution in the MoMA.
+Thirdly, linear models will be used to further analyze the MoMA's gender distribution and its changes over time.
+Finally, key findings, limitations, and next steps will be discussed.
 
 # Data {#sec-data}
-### Data Source
-In this report, the 25795 observations from the ____ and 65 observations from the _______ are used to investigate the level of diversity among MoMA decision-making directors and displayed artists.
-This data was obtained from the MoMA's publicly available GitHub, which has several public repositories containing data regarding the museum [@MoMAGithub].
-For this analysis, the MoMA GitHub repositories of ____ [@____] and ____ [@__] were used.
+
+## Data Source
+
+In this report, the 32,537 observations from the MoMA's exhibition index dataset and 65 observations from the directors and department heads dataset are used to investigate the level of diversity among MoMA decision-making directors and displayed artists.
+This data was obtained from the MoMA's publicly available GitHub, which has several public repositories containing data regarding the museum [@MoMAGitHub].
+For this analysis, the MoMA's "exhibitions" GitHub repository [@MoMAGitHubexhibitions] was used.
+The exhibition index dataset was created by a MoMA Archives team and contains information regarding the exhibitions featured in the MoMA from 1929 to 1989.
+The team is currently working on adding information on exhibits from 1990 onwards to the dataset.
+The directors and department heads dataset contains information regarding all of the directors of the entire museum and the department heads of curatorial departments within the museum from 1929 to the present.
 
@@
 For the results and analysis of this report, all figures were created using the tidyverse package [@tidyverse].
-Additionally, the tables were created using the packages knitr [@knitr] and kableExtra [@kableExtra], and the graphs were created using the packages tidyr [@tidyr] and ggplot2 [@ggplot2].
+Additionally, the tables were created using the packages knitr [@knitr] and kableExtra [@kableExtra], the graphs were created using the packages tidyr [@tidyr] and ggplot2 [@ggplot2], and the models were displayed using the modelsummary package [@modelsummary].
 
-### Variables of Interest
+## Variables of Interest
 
-Our report selects 7 variables for analysis.
-We focus on 6 particular factors that we predicted affects the amount of Internet use: age, sex, race, number of children, marital status, and happiness.
-In this paper, we investigate the influence of these various factors on the total number of hours of weekly Internet usage.
-The packages tidyverse [@tidyverse], haven [@haven], and reshape2 [@reshape2] were used to clean the dataset by grouping or converting the questionnaire responses into categorical or textual answers.
+This report selects 7 variables for analysis from the MoMA exhibition index dataset and 6 variables from the directors and department heads.
+Variables regarding social background, specifically gender and nationality, were chosen in order to measure diversity within the MoMA.
 
-The variables, Number of Children and Weekly Internet Hours, are recorded as a numerical value.
-Weekly Internet Hours has a maximum value of 168, as there are only 168 hours in a week.
-Age is also recorded as a numerical value, but is cleaned to represent ages in groups of ten years.
-The other variables, Sex, Race, Marital Status, and Happiness Level, are all recorded as a textual option for respondents to choose from.
+@tbl-exhibits shows the 7 variables of the MoMA exhibition index dataset and the first 10 rows of it, where each row represents a different individual constituent in the exhibit.
+The Exhibition Title variable refers to the exhibit name.
+The Name variable indicates the artist.
+Nationality indicates the individual's nationality (e.g.
+"American") and is investigated further in @_____.
+Gender has two options of "Male" or "Female".
+Exhibition Start and Exhibition End indicate the time period that the exhibit was displayed at the MoMA for, and are the only numerical variables in this dataset.
 
-Investigating artists:
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-exhibits
+#| tbl-cap: "First ten rows of the MoMA Exhibits dataset"
+#| warning: false
+
+cleaned_momaexhibit_data |> 
+  slice(1:10) |> 
+  knitr::kable(
+    col.names = c("Exhibition Title", "Artist Name", "Nationality", "Gender", "Exhibition Start", "Exhibition End"),
+    booktabs = TRUE,
+    linesep = ""
+  )
+```
+
+@tbl-directors shows the 6 variables of the MoMA directors and department heads dataset and the first 10 rows of it, where each row represents a different individual.
+The Department variable refers to the specific curatorial department within the MoMA that the individual is in charge of.
+As with the exhibition dataset, the Name variable indicates the person, Nationality indicates the individual's nationality (e.g.
+"American") and is investigated further in @_____, and Gender has two options of "Male" or "Female".
+Start and End indicate the time period that the individual held the position for, and are the only numerical variables in this dataset.
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-directors
+#| tbl-cap: "First ten rows of the MoMA Directors and Department Heads dataset"
+#| warning: false
+
+cleaned_momadirectors_data |> 
+  slice(1:10) |> 
+  knitr::kable(
+    col.names = c("Department", "Name", "Start", "End", "Nationality", "Gender"),
+    booktabs = TRUE,
+    linesep = ""
+  )
+```
+
+The data was cleaned and modified using the tidyverse package [@tidyverse].
+
+## Data Visualization
+
+The data was visualized as bar graphs in order to best understand the distribution of the diversity indicators in the data (i.e. the Gender and Nationality variables).
+
+@fig-artistnationality displays the nationality distribution of the artists whose works have been displayed in exhibits in the MoMA.
+Aside from the large number of missing values (marked as NA at the rightmost bar), the most common nationality among is American, at 14,112 artists.
+The second highest nationality is French, at 3,747 artists - nearly a fifth of the American artists.
+The large number of American artists may be explained in part because the MoMA itself is American.
+It is surprising though that while the MoMA has presented 2,500+ exhibits throughout its history, \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_.
 
@@
 cleaned_momaexhibit_data |>
-  filter(ExhibitionRole == "Artist") |>
   ggplot(mapping = aes(x = Nationality)) +
@@
   geom_bar(position = "dodge2")+
-  labs(x = "Nationality", y = "Count of Artists in MoMA Exhibits") 
+  labs(x = "Nationality", y = "Number of Artists in MoMA Exhibits") 
 ```
@@
 \newpage
+
+@fig-artistgender displays the gender distribution of the artists whose works have been displayed in exhibits in the MoMA.
+As the graph demonstrates, there is a much larger number of male artists who have been featured in the MoMA exhibits than female artists.
+With 22,518 male artists and 2,301 female artists, the male to female ratio is approximately 10:1, showing significant inequality in gender representation in MoMA artists.
+This may be partly explained by _____.
 
@@
 cleaned_momaexhibit_data |> 
-  filter(ExhibitionRole == "Artist") |>
   count(Gender) |>
@@
 
-Investigating directors and department heads:
+@fig-staffnationality displays the nationality distribution of all of the directors and department heads at the MoMA.
+Here too, like in the nationality distribution of artists, there is a majority of American nationality among the directors and department heads, at 50 Americans.
+Compared to the 3 Swiss, 3 British, 2 German, 1 French, and 1 Austrian directors and department heads, \_\_\_\_\_\_\_\_\_\_.
 
@@
 \newpage
+
+@fig-staffgender displays the gender distribution of all of the directors and department heads at the MoMA.
+Here too, there are many more male directors and department heads compared to female department heads.
+With 53 male directors and department heads and 12 female directors and department heads, the male to female ratio is approximately 4:1, showing inequality in gender representation in MoMA leadership.
+This may be partly explained by \_\_\_\_\_\_\_\_\_\_.
 
@@
 # Model
+
 From the exploratory data analysis above, it is clear that both the number of female MoMA directors and the number of female artists displayed in the MoMA is much less than the number of male counterparts in these positions.
@@
 Here we briefly describe the three linear regression models used to investigate this relationship between gender and time.
-Background details and diagnostics are included in [Appendix -@sec-model-details].
 
 ## Model Set-Up
-The first linear regression model regarding the effect of time on the percentage of female MoMA directors is as follows:
-$$\hat{y} = \beta_0 + \beta_1x_{year}$$
+
+The first linear regression model regarding the effect of time on the percentage of female MoMA directors is as follows: $$\hat{y} = \beta_0 + \beta_1x_{year}$$
 
@@
 
-* Percentage of female MoMA directors, the response variable, is used as a quantitative measure of gender diversity that is between 0 and 100
+-   Percentage of female MoMA directors, the response variable, is used as a quantitative measure of gender diversity that is between 0 and 100
 
-* Year, the explanatory variable, is a numeric variable between 1929 (the founding year of the MoMA) and 2023 (the year that this report was published) indicating a specific year in the history of the MoMA
+-   Year, the explanatory variable, is a numeric variable between 1929 (the founding year of the MoMA) and 2023 (the year that this report was published) indicating a specific year in the history of the MoMA
 
-The second linear regression model regarding the effect of time on the percentage of female MoMA artists in the exhibits is similar to the first and is as follows:
-$$\hat{y} = \beta_0 + \beta_1x_{year}$$
+The second linear regression model regarding the effect of time on the percentage of female MoMA artists in the exhibits is similar to the first and is as follows: $$\hat{y} = \beta_0 + \beta_1x_{year}$$
 
@@
 
-* Percentage of female MoMA artists, the response variable, is used as a quantitative measure of gender diversity that is between 0 and 100
+-   Percentage of female MoMA artists, the response variable, is used as a quantitative measure of gender diversity that is between 0 and 100
 
-* Year, the explanatory variable, is a numeric variable between 1929 (the founding year of the MoMA) and 1990 (the year that the MoMA public GitHub has data until) indicating a specific year in the history of the MoMA
+-   Year, the explanatory variable, is a numeric variable between 1929 (the founding year of the MoMA) and 1990 (the year that the MoMA public GitHub has data until) indicating a specific year in the history of the MoMA
 
-The third and final linear regression model differs slightly from the previous two and is as follows:
-$$\hat{y} = \beta_0 + \beta_1x_{femaledirectorpercentage} + \beta_2x_{year}$$
+The third and final linear regression model differs slightly from the previous two and is as follows: $$\hat{y} = \beta_0 + \beta_1x_{femaledirectorpercentage} + \beta_2x_{year}$$
 
@@
 
-* Percentage of female MoMA artists, the response variable, is used as a quantitative measure of gender diversity that is between 0 and 100
+-   Percentage of female MoMA artists, the response variable, is used as a quantitative measure of gender diversity that is between 0 and 100
 
-* Percentage of female MoMA directors, an explanatory variable, is a numeric variable between 0 and 100 indicating the gender distribution of the directors who had the decision-making power to choose the artists to be displayed
+-   Percentage of female MoMA directors, an explanatory variable, is a numeric variable between 0 and 100 indicating the gender distribution of the directors who had the decision-making power to choose the artists to be displayed
 
-* Year, an explanatory variable, is a numeric variable between 1929 (the founding year of the MoMA) and 2023 (the year that this report was published) indicating a specific year in the history of the MoMA
+-   Year, an explanatory variable, is a numeric variable between 1929 (the founding year of the MoMA) and 2023 (the year that this report was published) indicating a specific year in the history of the MoMA
 
-All of the models are run in R [@citeR] using the `stats` package of @stats.
+All of the models are run in R [@R] and displayed using modelsummary [@modelsummary].
 
-### Model justification
+### Model Justification
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+For the first two models regarding the effect of time on the percentage of female MoMA directors and on artists, time was chosen to be evaluated because there has been an increased push for gender equality in workplaces across the United States over the years.
+Because of this, a positive relationship between time in years and the percentage of female directors and female artists is expected for both the first linear regression model (regarding the effect of time on the percentage of female MoMA directors) and the second linear regression model (regarding the effect of time on the percentage of female MoMA artists).
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+Given these two models, it is worth investigating whether there is a relationship between the percentage of female directors and the percentage of female artists, to determine whether female directors are more likely to be aware of gender inclusion and thus display more female artists than their male counterparts.
+Because women are subjects of workplace gender discrimination, they are more likely to be aware of the need for inclusive gender representation, so a positive relationship between time in years and the percentage of female directors and female artists is expected.
 
@@
 
-\appendix
-
-# Appendix {.unnumbered}
-
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-#pp_check(first_model) +
-#  theme_classic() +
-#  theme(legend.position = "bottom")
-#posterior_vs_prior(first_model) +
-#  theme_minimal() +
-#  scale_color_brewer(palette = "Set1") +
-#  theme(legend.position = "bottom") +
-#  coord_flip()
-```
-
-## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-#plot(first_model, "trace")
-#plot(first_model, "rhat")
-```
-
-\newpage
-
 # References

### 2023-04-19 scripts/00-simulate_data.R
Edited models and the simulated data

@@ -11,6 +11,7 @@ library(tidyverse)
 
 
 #### Simulate data ####
+# Create dataset with: year, percentage of female artists, percentage of non-white artists, and the position of the individual in the MoMA exhibit
 set.seed(853)
 
 artists_simulated_data <-
@@ -20,17 +21,17 @@ artists_simulated_data <-
       n = 95, 
       min = 0, 
       max = 100),
-    race = sample(
-      x = c(1:7),
-      size = 95,
-      replace = TRUE),
+    percentage_notwhite = runif(
+      n = 95, 
+      min = 0, 
+      max = 100),
     position = sample(
       x = c("Artist"),
       size = 95,
       replace = TRUE)
  )
-head(artists_simulated_data)
 
+# Create dataset with: year, percentage of female directors or department head, percentage of non-white directors or department head, and the position of the individual in MoMA
 directors_simulated_data <-
   tibble(
     year = c(1929:2023),
@@ -38,16 +39,15 @@ directors_simulated_data <-
       n = 95, 
       min = 0, 
       max = 100),
-    race = sample(
-      x = c(1:7),
-      size = 95,
-      replace = TRUE),
+    percentage_notwhite = runif(
+      n = 95, 
+      min = 0, 
+      max = 100),
     position = sample(
       x = c("Director or Department Head"),
       size = 95,
       replace = TRUE)
   )
-head(directors_simulated_data)
 
 
 #### Save simulated data ####

### 2023-04-19 scripts/02-clean_data.R

@@ -46,6 +46,15 @@ cleaned_momaexhibit_data <-
 cleaned_momaexhibit_data <- 
   cleaned_momaexhibit_data |> 
   select(ExhibitionTitle, DisplayName, Nationality, Gender, StartYear, Year)
+
+# Remove NAs from both datasets 
+cleaned_momaexhibit_data <- 
+  cleaned_momaexhibit_data |> 
+  drop_na()
+
+cleaned_momadirectors_data <- 
+  cleaned_momadirectors_data |> 
+  drop_na()
          
 
 # Edit gender variable to remove duplicates and null from Exhibit

### 2023-04-19 scripts/03-test_data.R

@@ -19,6 +19,9 @@ directors_simulated_data <- read_csv("outputs/data/directors_simulated_data.csv"
 artists_simulated_data$percentage_female |> 
   class() == "numeric"
 
+artists_simulated_data$percentage_notwhite |> 
+  class() == "numeric"
+
 artists_simulated_data$year |> 
   class() == "numeric"
 
@@ -32,4 +35,10 @@ directors_simulated_data$percentage_female |>
   min() >= 0
 
 directors_simulated_data$percentage_female |> 
+  max() <= 100
+
+directors_simulated_data$percentage_notwhite |> 
+  min() >= 0
+
+directors_simulated_data$percentage_notwhite |> 
   max() <= 100

### 2023-04-19 outputs/paper/paper.qmd
Wrote a draft of the analysis paper

@@
 ---
-title: "How Diverse is the MoMA: While Modern, Not Diverse in Its Artists and Directors"
-subtitle: "An analysis of the MoMA's public datasets on their collections and exhibits"
+title: "Investigating the Gender and Nationality Distributions of the MoMA: While Modern, Not Diverse in Its Artists and Decision-making Staff"
+subtitle: "An analysis of the MoMA's public datasets"
 author: Sakura Ariga
@@
 date-format: "D MMMM YYYY"
-abstract: "The MoMA's public GitHub data on their exhibits and collections was analyzed to determine how diverse the artists and directors at the MoMA are.
-It was found that the MoMA is comprised largely of white men, but that this relationship has changed with time.
-This finding gives quantitative proof of the need for more representation within not jus the MoMA, but all American museums as a whole."
+abstract: "The MoMA's public GitHub data on their exhibits and collections was analyzed to determine how diverse the artists and directors at the MoMA are in terms of gender and nationality.
+It was found that the MoMA is comprised largely of American men and particularly lacking in their representation of women, both as artists and as directors and department heads.
+However, it was found that women representation has a positive relationship with time, indicating that the MoMA's gender distribution has improved slightly over time.
+This finding gives quantitative proof of the need for more gender representation in the MoMA, both in the artists displayed and in the top decision-making staff hired."
 format: pdf
+toc: true
 number-sections: true
@@
 It was found that the MoMA's artists and directors were predominantly men.
-Simple linear regression models show that time affects this percentage of female artists, directors, and department heads in that the number of female artists has increased on average by ___ percentage points per year, while the number of female directors and department heads has increased on average by 0.25 percentage points per year.
+Simple linear regression models show that time affects this percentage of female artists, directors, and department heads in that the number of female artists has increased on average by 0.08 percentage points per year, while the number of female directors and department heads has increased on average by 0.24 percentage points per year.
+It was also found that the percentage of female directors and department heads has a positive relationship with the percentage of female artists displayed, with an increase of an average of 0.10 percentage points in women artists with every 1% increase of women directors and department heads.
 These findings are important because they provide numerical proof of the lack of gender diversity in the MoMA, both in the artists displayed and in the directors and department heads who choose the artists to display, which could motivate the MoMA to take active steps to better the gender representation within their institution.
@@
 Nationality indicates the individual's nationality (e.g.
-"American") and is investigated further in @_____.
-Gender has two options of "Male" or "Female".
+"American") and Gender has two options of "Male" or "Female".
 Exhibition Start and Exhibition End indicate the time period that the exhibit was displayed at the MoMA for, and are the only numerical variables in this dataset.
-
+\newpage
 ```{r}
@@
 
+# Create table of first ten rows of the cleaned_momaexhibit_data to explain variables 
 cleaned_momaexhibit_data |> 
@@
     linesep = ""
-  )
+  ) |>
+  kable_styling(latex_options="scale_down")
 ```
@@
 As with the exhibition dataset, the Name variable indicates the person, Nationality indicates the individual's nationality (e.g.
-"American") and is investigated further in @_____, and Gender has two options of "Male" or "Female".
+"American"), and Gender has two options of "Male" or "Female".
 Start and End indicate the time period that the individual held the position for, and are the only numerical variables in this dataset.
@@
 
+# Create table of first ten rows of the cleaned_momadirectors_data to explain variables 
 cleaned_momadirectors_data |> 
@@
 The large number of American artists may be explained in part because the MoMA itself is American.
-It is surprising though that while the MoMA has presented 2,500+ exhibits throughout its history, \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_.
 
@@
 
-# Bar graph showing nationality distribution of Artists in MoMA exhibits
+# Bar graph showing nationality distribution of artists displayed in MoMA exhibits
 cleaned_momaexhibit_data |>
   ggplot(mapping = aes(x = Nationality)) +
-  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
-  geom_bar(position = "dodge2")+
+  theme(axis.text.x = element_text(angle = 90, hjust=1, size = 5)) +
+  geom_bar(position = "dodge2", fill = "cornflowerblue")+
   labs(x = "Nationality", y = "Number of Artists in MoMA Exhibits") 
@@
 With 22,518 male artists and 2,301 female artists, the male to female ratio is approximately 10:1, showing significant inequality in gender representation in MoMA artists.
-This may be partly explained by _____.
 
@@
 
-# Bar graph showing gender distribution of Artists in MoMA exhibits
+# Bar graph showing gender distribution of artists displayed in MoMA exhibits
 cleaned_momaexhibit_data |> 
@@
   ggplot(mapping = aes(x = Gender, y = n)) +
-  geom_col() + 
+  geom_col(fill = "mediumorchid") + 
   theme(axis.text.x = element_text(angle = 90, hjust=1)) +
@@
 @fig-staffnationality displays the nationality distribution of all of the directors and department heads at the MoMA.
-Here too, like in the nationality distribution of artists, there is a majority of American nationality among the directors and department heads, at 50 Americans.
-Compared to the 3 Swiss, 3 British, 2 German, 1 French, and 1 Austrian directors and department heads, \_\_\_\_\_\_\_\_\_\_.
+Here too, like in the nationality distribution of artists, there is a majority of American nationality among the directors and department heads, at 50 out of 60 Americans.
 
@@
   theme(axis.text.x = element_text(angle = 90, hjust=1)) +
-  geom_bar(position = "dodge2")+
+  geom_bar(position = "dodge2", fill = "cornflowerblue")+
   labs(x = "Nationality", y = "Count of MoMA Directors and Department Heads") 
@@
 With 53 male directors and department heads and 12 female directors and department heads, the male to female ratio is approximately 4:1, showing inequality in gender representation in MoMA leadership.
-This may be partly explained by \_\_\_\_\_\_\_\_\_\_.
 
@@
   theme(axis.text.x = element_text(angle = 90, hjust=1)) +
-  geom_bar(position = "dodge2")+
+  geom_bar(position = "dodge2", fill = "mediumorchid")+
   labs(x = "Gender", y = "Count of MoMA Directors and Department Heads")
@@
 
-### Model Justification
+## Model Justification
 
@@
 # Results
-
-Our results are summarized in @tbl-modelresults.
+The results of the first linear regression model of the effect of time on the percentage of female MoMA directors is summarized in @tbl-modelresults1.
+The prediction of a positive relationship between time in years and the percentage of female MoMA directors proved correct, with the percentage of female directors increasing every year by 0.25 percentage points since the MoMA's founding in 1929.
+We know that this finding is significant because the p-value of this model is less than the threshold of 0.05.
+@fig-model1 demonstrates this  relationship as a scatterplot, better visualizing the positive linear relationship between the amount of women leaders in the MoMA and time.
 
 ```{r}
-#| label: fig-model1
-#| fig-cap: Linear regression model of the effect of time on the percentage of female MoMA directors
 #| echo: false
@@
 
+# Import linear regression model of the effect of time on percentage of female MoMA directors
 model_directors_percentage_female <-
@@
 
+# Table showing results of model of the effect of time on percentage of female MoMA directors
 modelsummary::modelsummary(
@@
 ```{r}
-#| label: fig-model2
-#| fig-cap: Linear regression model of the effect of exhibit year on the percentage of female MoMA artists
+#| label: fig-model1
+#| fig-cap: Linear model of percentage of female MoMA directors by year
+#| echo: false
+#| warning: false
+
+model_directors_percentage_female |>
+  ggplot(aes(x = Year, y = PercentageFemale)) +
+  geom_point(alpha = 0.5) +
+  geom_smooth(
+    method = "lm",
+    se = TRUE,
+    color = "black",
+    linetype = "dashed",
+    formula = "y ~ x"
+  ) +
+  labs(
+    x = "Time (Years)",
+    y = "Percentage of Female MoMA Directors"
+  ) 
+```
+\newpage
+The results of the second linear regression model of the effect of time on the percentage of female MoMA artists is summarized in @tbl-modelresults2.
+The prediction of a positive relationship between time in years and the percentage of female MoMA artists proved correct, with the percentage of female artists increasing every year by 0.08 percentage points since the MoMA's founding in 1929.
+This finding is significant because the p-value of this model is less than the threshold of 0.05.
+@fig-model2 demonstrates this  relationship as a scatterplot, better visualizing the positive linear relationship between the amount of women artists who have been displayed in MoMA exhibits and time.
+```{r}
 #| echo: false
@@
 
+# Import linear regression model of the effect of time on percentage of female MoMA artists
 model_exhibits_percentage_female <-
@@
 
+# Table showing results of model of the effect of time on percentage of female MoMA artists
 modelsummary::modelsummary(
@@
 ```{r}
-#| label: fig-model3
-#| fig-cap: Linear regression model of the effect of time and percentage of female MoMA directors on the percentage of female MoMA artists selected for exhibits
+#| label: fig-model2
+#| fig-cap: Linear model of percentage of female MoMA artists by year
+#| echo: false
+#| warning: false
+
+model_exhibits_percentage_female |>
+  ggplot(aes(x = Year, y = PercentageFemale)) +
+  geom_point(alpha = 0.5) +
+  geom_smooth(
+    method = "lm",
+    se = TRUE,
+    color = "black",
+    linetype = "dashed",
+    formula = "y ~ x"
+  ) +
+  labs(
+    x = "Time (Years)",
+    y = "Percentage of Female MoMA Artists"
+  ) 
+```
+
+\newpage
+
+The results of the third linear regression model of the effect of time and the percentage of female MoMA directors on the percentage of female MoMA artists is summarized in @tbl-modelresults3.
+The prediction of a positive relationship between time in years and the percentage of female directors and the percentage of female MoMA artists proved correct, with the percentage of female artists increasing by 0.10 percentage points with every 1% increase in the percentage of female directors.
+```{r}
 #| echo: false
@@
 
+# Import linear regression model of the effect of time and percentage of female MoMA directors on percentage of female MoMA artists
 model_exhibits_on_directors <-
@@
 
+# Table showing results of model of the effect of time and percentage of female MoMA directors on percentage of female MoMA artists
 modelsummary::modelsummary(
@@
 
+\newpage
+
 # Discussion
 
-## Gender distribition {#sec-first-point}
+## Gender Distribution 
+From @fig-artistgender and @fig-staffgender, we see that there is a significant gap between representation of men versus women in the MoMA, both for the artists displayed and for the museum staff with the most power.
+Comparing @fig-artistgender and @fig-staffgender, the men:women ratio is more unequal in the artists, at a ratio of 10:1, than in the directors and department heads, at a ratio of 4:1.
 
-## Nationality distribition {#sec-second-point}
+This distribution is surprising, especially given that the MoMA was founded due to the works and ideas of women: Lillie P.
+Bliss, Mary Quinn Sullivan, and Abby Aldrich Rockefeller - three influential women who were patrons of the arts in the 1920s [@MoMA].
+One potential reason for this could be American society's historical attitude towards women versus men, tending to elevate and encourage men to pursue careers as artists or museum curators and discouraging women to.
+Another reason could be related to the findings of the third model found in @tbl-modelresults3: if women directors and department heads are more likely to choose women artists' work to exhibit, the same may go for men directors and department heads with men artists.
+These two reasons could be related to each other as well, with male directors and department heads more likely to choose male artists due to social conditioning from society's expectations of gender roles.
 
-## Analyzing the model: is time a factor? {#sec-third-point}
+While the above models (found in @fig-model1, @fig-model2, @tbl-modelresults3) show that change has occurred and that the percentage of women represented in the MoMA's displayed artists and decision-making staff has increased over time, there is still much more room for improvement.
+As an institution with "modern" in its name, the MoMA should act as a role model for other cultural institutions and be an active leader in incorporating more diversity in the museum, both in showcasing more female artists and in hiring more female directors and department heads.
+This holds true especially now that it has been nearly a century since the MoMA's opening and thus much more modern art has been created and can be displayed.
 
-## Comparing artists vs directors {#sec-fourth-point}
+## Nationality Distribution 
+@fig-artistnationality and @fig-staffnationality show us that the museum is predominantly made up of American representation, both in its artists and in its decision-making staff.
+Most interesting is that the nationalities most represented in the artists is also represented well in the directors and department heads: American, French, British.
+One possible explanation of this is that these three countries place a heavy emphasis on the modern arts, and so produce many artists and museum staff.
+Another explanation could be that the MoMA places a eurocentric, Western-heavy emphasis on their exhibits, and thus is biased towards selecting American, French, and British artists and staff.
+Because nationality is not the best indicator for social inclusion practices, analysis on racial discrimination cannot be made here from this data.
 
-## Weaknesses and next steps
+## Weaknesses and Next Steps
+One weakness of this analysis is the binary understanding of gender as only male or female.
+This excludes artists, directors, and department heads who do not identify within this gender binary and thus this analysis was not able to completely measure gender diversity in the MoMA.
+Another bias present in this analysis is the removal of missing values that occurred during the data cleaning step of this paper, which made up a large number of responses, particularly in the gender of artists.
+This inevitably led to the results of the gender distribution analysis being biased and not entirely accurate.
 
--   a LOT of NAs in the exhibit dataset, especially regarding artist gender, so results are skewed bc of that
--   binary understanding of gender that is exclusive
+Thus, an appropriate next step would be to conduct more research on the demographics of the artists, directors, and department heads of the MoMA so that a more accurate and meaningful analysis can be conducted.
+Not only would this account for some of the missing values that were excluded in this paper, this could result in analysis on racial equality in the MoMA.
+While the nationality variable that was analyzed in this paper was helpful in understanding some aspect of inclusion in the MoMA, in a museum that is so dominated by Americans, both as artists and as decision-making museum staff, an analysis on the racial representation in the MoMA would yield more actionable insights.
 

### 2023-04-20 scripts/02-clean_data.R
Fixed formatting and removed unused code chunks

@@ -62,6 +62,9 @@ cleaned_momadirectors_data <-
 #   cleaned_momaexhibit_data |>
 #   filter(Gender == "Female" | Gender == "Male")
 
+cleaned_momaexhibit_data <- 
+  cleaned_momaexhibit_data[Gender == 'Female']
+
 #### Save data ####
 write_csv(cleaned_momaexhibit_data, "outputs/data/cleaned_momaexhibit_data")
 write_csv(cleaned_momadirectors_data, "outputs/data/cleaned_momadirectors_data")

### 2023-04-20 scripts/03-test_data.R

@@ -18,27 +18,19 @@ directors_simulated_data <- read_csv("outputs/data/directors_simulated_data.csv"
 #### Test data ####
 artists_simulated_data$percentage_female |> 
   class() == "numeric"
-
 artists_simulated_data$percentage_notwhite |> 
   class() == "numeric"
-
 artists_simulated_data$year |> 
   class() == "numeric"
-
 artists_simulated_data$year |> 
   min() == 1929
-
 directors_simulated_data$year |> 
   max() == 2023
-
 directors_simulated_data$percentage_female |> 
   min() >= 0
-
 directors_simulated_data$percentage_female |> 
   max() <= 100
-
 directors_simulated_data$percentage_notwhite |> 
   min() >= 0
-
 directors_simulated_data$percentage_notwhite |> 
   max() <= 100

### 2023-04-20 scripts/04-model_data.R

@@ -8,7 +8,11 @@
 
 #### Workspace setup ####
 library(tidyverse)
-library(rstanarm)
+
+
+#### Download data ####
+cleaned_momaexhibit_data <- read_csv("outputs/data/cleaned_momaexhibit_data")
+cleaned_momadirectors_data <- read_csv("outputs/data/cleaned_momadirectors_data")
 
 
 #### Model 1 ####
@@ -74,13 +78,6 @@ summary(model_exhibits_percentage_female)
 #### Model 3 ####
 merged_gender_percentage <- 
   left_join(exhibits_gender_percentage, directors_gender_percentage, by = "Year")
-
-# merged_gender_percentage <- 
-#   merged_gender_percentage |> 
-#   rename = ("PercentageMaleArtists" = "PercentageMale.x")
-#             "PercentageFemaleArtists" = "PercentageFemale.x",
-#             "PercentageMaleDirectors" = "PercentageMale.y",
-#             "PercentageFemaleDirectors" = "PercentageFemale.y")
 
 model_exhibits_on_directors <- 
   lm(

### 2023-04-20 scripts/02-clean_data.R
Removed unused code

@@ -55,15 +55,6 @@ cleaned_momaexhibit_data <-
 cleaned_momadirectors_data <- 
   cleaned_momadirectors_data |> 
   drop_na()
-         
-
-# Edit gender variable to remove duplicates and null from Exhibit
-# cleaned_momaexhibit_data <- 
-#   cleaned_momaexhibit_data |>
-#   filter(Gender == "Female" | Gender == "Male")
-
-cleaned_momaexhibit_data <- 
-  cleaned_momaexhibit_data[Gender == 'Female']
 
 #### Save data ####
 write_csv(cleaned_momaexhibit_data, "outputs/data/cleaned_momaexhibit_data")

### 2023-04-20 outputs/paper/paper.qmd
Wrote final draft of paper

@@
 title: "Investigating the Gender and Nationality Distributions of the MoMA: While Modern, Not Diverse in Its Artists and Decision-making Staff"
-subtitle: "An analysis of the MoMA's public datasets"
+subtitle: "An analysis of the Museum of Modern Art's public datasets"
 author: Sakura Ariga
@@
 
-Diversity in cultural institutions is a topic that is increasingly being discussed and raised as a problem to be tackled, in museums in particular [@museumnext].
+Diversity in cultural institutions is a topic that is increasingly being discussed and raised as a problem to be tackled, especially in museums [@museumnext].
 While the main goal of museums is to serve as cultural institutions and a place of learning, oftentimes the objects on display or the decision-making staff who work behind the scenes do not meet this mission of inclusion.
 
-This paper will investigate the level of diversity in one such museum: the Museum of Modern Art (also known as MoMA).
+This paper will investigate the level of diversity in one such museum: the Museum of Modern Art (also known as MoMA) in New York of the United States.
 Founded in 1929, the MoMA, as its name suggests, houses a collection of contemporary art pieces.
-It was originally created to go against traditional art museums by housing only modern art, and has since grown to become an influential cultural institution [@MoMA].
+It was originally created to go against traditional art museums by housing only modern art, and has since grown to become an influential authority in the art world [@MoMA].
 Using data made publicly available on the MoMA's GitHub account, this paper aims to evaluate how diverse the artists of the artworks on display are, as well as how diverse the directors and department heads who chose to display these artworks are, in terms of gender and nationality.
-Thus, the estimand is: the percentage of artists, directors, and department heads in the MoMA's history who are / were not white men.
+Thus, the estimand is: the percentage of artists, directors, and department heads in the MoMA's history who are / were not American men.
 
-It was found that the MoMA's artists and directors were predominantly men.
+This paper found that the MoMA's artists, directors, and department heads were predominantly men, with a much smaller percentage of women representation present.
 Simple linear regression models show that time affects this percentage of female artists, directors, and department heads in that the number of female artists has increased on average by 0.08 percentage points per year, while the number of female directors and department heads has increased on average by 0.24 percentage points per year.
@@
 
-This paper's structure will begin by explaining the MoMA's publicly made available data regarding its artists and staff that is the subject of analysis.
+This paper will begin by explaining the MoMA's public data regarding its artists and staff that are the subject of analysis.
 It will then explore this data to understand overall trends in nationality and gender distribution in the MoMA.
-Thirdly, linear models will be used to further analyze the MoMA's gender distribution and its changes over time.
+Thirdly, linear models will be used to further analyze gender distribution and its changes over time.
 Finally, key findings, limitations, and next steps will be discussed.
@@
 
-In this report, the 32,537 observations from the MoMA's exhibition index dataset and 65 observations from the directors and department heads dataset are used to investigate the level of diversity among MoMA decision-making directors and displayed artists.
+In this report, 32,537 observations from the MoMA's exhibition index dataset and 65 observations from the directors and department heads dataset are used to investigate the level of diversity among MoMA decision-making staff and displayed artists.
 This data was obtained from the MoMA's publicly available GitHub, which has several public repositories containing data regarding the museum [@MoMAGitHub].
@@
 
-This report was created using the R statistical programming language [@R].
-For the results and analysis of this report, all figures were created using the tidyverse package [@tidyverse].
-Additionally, the tables were created using the packages knitr [@knitr] and kableExtra [@kableExtra], the graphs were created using the packages tidyr [@tidyr] and ggplot2 [@ggplot2], and the models were displayed using the modelsummary package [@modelsummary].
+This report was created using the R statistical programming language [@R] and all figures were created using the tidyverse package [@tidyverse].
+Additionally, the tables were created using the packages knitr [@knitr] and kableExtra [@kableExtra], the graphs using the packages tidyr [@tidyr] and ggplot2 [@ggplot2], and the models using the modelsummary package [@modelsummary].
 
@@
 
-This report selects 7 variables for analysis from the MoMA exhibition index dataset and 6 variables from the directors and department heads.
+This report selects 6 variables for analysis from the MoMA exhibition index dataset and 6 variables from the directors and department heads.
 Variables regarding social background, specifically gender and nationality, were chosen in order to measure diversity within the MoMA.
 
-@tbl-exhibits shows the 7 variables of the MoMA exhibition index dataset and the first 10 rows of it, where each row represents a different individual constituent in the exhibit.
+@tbl-exhibits shows the 6 variables of the MoMA exhibition index dataset and the first 10 rows of it, where each row represents a different individual artist.
 The Exhibition Title variable refers to the exhibit name.
@@
 "American") and Gender has two options of "Male" or "Female".
-Exhibition Start and Exhibition End indicate the time period that the exhibit was displayed at the MoMA for, and are the only numerical variables in this dataset.
-\newpage
+Exhibition Start and Exhibition End indicate the time period that the exhibit was displayed at the MoMA for.
+These latter two variables were created by extracting only the year of the original ExhibitionBeginDate and ExhibitionEndDate variables.
+
 ```{r}
@@
 #| label: tbl-exhibits
-#| tbl-cap: "First ten rows of the MoMA Exhibits dataset"
+#| tbl-cap: "First ten rows of the Artists in MoMA Exhibits dataset"
 #| warning: false
@@
 Start and End indicate the time period that the individual held the position for, and are the only numerical variables in this dataset.
+NA values in the End variables were replaced with the current year (2023, as of the time that this paper was written) as they were assumed to mean that the individual's position period was still continuing and thus are still employed at the museum at the time of writing of this paper.
 
@@
 
-The data was cleaned and modified using the tidyverse package [@tidyverse].
-
 ## Data Visualization
@@
 @fig-artistnationality displays the nationality distribution of the artists whose works have been displayed in exhibits in the MoMA.
-Aside from the large number of missing values (marked as NA at the rightmost bar), the most common nationality among is American, at 14,112 artists.
+Aside from the large number of missing values (marked as NA at the rightmost bar), the most common nationality among MoMA artists is American, at 14,112 artists.
 The second highest nationality is French, at 3,747 artists - nearly a fifth of the American artists.
@@
   geom_bar(position = "dodge2", fill = "cornflowerblue")+
-  labs(x = "Nationality", y = "Number of Artists in MoMA Exhibits") 
+  labs(x = "Nationality", y = "Number of Artists")
 ```
@@
 As the graph demonstrates, there is a much larger number of male artists who have been featured in the MoMA exhibits than female artists.
-With 22,518 male artists and 2,301 female artists, the male to female ratio is approximately 10:1, showing significant inequality in gender representation in MoMA artists.
+With 22,518 male artists and 2,301 female artists, the male to female ratio is approximately 10:1, showing significant inequality in terms of gender representation in MoMA artists.
 
@@
   count(Gender) |>
+  filter(Gender == "Female" | Gender == "Male") |> 
   ggplot(mapping = aes(x = Gender, y = n)) +
@@
   theme(axis.text.x = element_text(angle = 90, hjust=1)) +
-  labs(x = "Gender", y = "Count of Artists in MoMA Exhibits") 
+  labs(x = "Gender", y = "Number of Artists") 
 ```
@@
 @fig-staffnationality displays the nationality distribution of all of the directors and department heads at the MoMA.
-Here too, like in the nationality distribution of artists, there is a majority of American nationality among the directors and department heads, at 50 out of 60 Americans.
+Here too, like in the nationality distribution of artists, there is a majority of American nationality among the directors and department heads, at 50 Americans out of the 60 directors and department heads.
 
@@
 #| label: fig-staffnationality
-#| fig-cap: Nationality Distribution of Directors and Department Heads in MoMA
+#| fig-cap: Nationality Distribution of Directors and Department Heads in the MoMA
 #| echo: false
@@
   geom_bar(position = "dodge2", fill = "cornflowerblue")+
-  labs(x = "Nationality", y = "Count of MoMA Directors and Department Heads") 
+  labs(x = "Nationality", y = "Number of MoMA Directors 
+       and Department Heads") 
 ```
@@
 @fig-staffgender displays the gender distribution of all of the directors and department heads at the MoMA.
-Here too, there are many more male directors and department heads compared to female department heads.
+Here too, there are many more male directors and department heads compared to female directors and department heads.
 With 53 male directors and department heads and 12 female directors and department heads, the male to female ratio is approximately 4:1, showing inequality in gender representation in MoMA leadership.
@@
 #| label: fig-staffgender
-#| fig-cap: Gender Distribution of Directors and Department Heads in MoMA
+#| fig-cap: Gender Distribution of Directors and Department Heads in the MoMA
 #| echo: false
@@
   geom_bar(position = "dodge2", fill = "mediumorchid")+
-  labs(x = "Gender", y = "Count of MoMA Directors and Department Heads")
+  labs(x = "Gender", y = "Number of MoMA Directors and
+       Department Heads")
 ```
@@
 
-From the exploratory data analysis above, it is clear that both the number of female MoMA directors and the number of female artists displayed in the MoMA is much less than the number of male counterparts in these positions.
+From the exploratory data analysis above, it is clear that both the number of female MoMA leadership staff and the number of female artists displayed in the MoMA is much less than the number of male counterparts in these positions.
 This gender relationship is worth further investigation using linear models.
@@
 The goal of this modelling strategy is threefold.
-Firstly, the relationship between the percentage of female directors at the MoMA and years will be investigated to determine whether the gender distribution of those who have the highest decision-making power at the MoMA has improved over time.
+Firstly, the relationship between the percentage of female directors / department heads at the MoMA and years will be investigated to determine whether the gender distribution of those who have the highest decision-making power at the MoMA has improved over time.
 Secondly, another model will look at the relationship between the percentage of female artists in exhibits at the MoMA and years to determine whether the gender distribution of the artists displayed in MoMA exhibits has improved over time.
-Finally, the third model will investigate the effect that female director percentage in the MoMA has on female artist percentage in MoMA exhibits to determine whether the gender distribution of top MoMA decision-makers has an effect on the gender distribution of artists selected for exhibits.
+Finally, the third model will investigate the effect that female director / department heads percentage in the MoMA has on female artist percentage in MoMA exhibits to determine whether the gender distribution of top MoMA decision-makers has an effect on the gender distribution of artists selected for exhibits.
 
@@
 
-The first linear regression model regarding the effect of time on the percentage of female MoMA directors is as follows: $$\hat{y} = \beta_0 + \beta_1x_{year}$$
+The first linear regression model regarding the effect of time on the percentage of female MoMA directors / department heads is as follows: $$\hat{y} = \beta_0 + \beta_1x_{year}$$
 
-The output of this linear regression model gives the percentage of female MoMA directors.
-Thus, the response in the model is the percentage of female MoMA directors based on the year explanatory variable.
+The output of this linear regression model gives the percentage of female MoMA directors and department heads.
+Thus, the response in the model is the percentage of female MoMA directors and department heads based on the year explanatory variable.
 A linear regression model was used because both the response variable and the explanatory variable are quantitative.
 
-This model focuses on the following two aspects of MoMA directors:
+This model focuses on the following two aspects of MoMA directors and department heads:
 
--   Percentage of female MoMA directors, the response variable, is used as a quantitative measure of gender diversity that is between 0 and 100
+-   Percentage of female MoMA directors and department heads, the response variable, is used as a quantitative measure of gender diversity that is between 0 and 100
 
@@
 
-The second linear regression model regarding the effect of time on the percentage of female MoMA artists in the exhibits is similar to the first and is as follows: $$\hat{y} = \beta_0 + \beta_1x_{year}$$
+The second linear regression model regarding the effect of time on the percentage of female MoMA artists in exhibits is similar to the first and is as follows: $$\hat{y} = \beta_0 + \beta_1x_{year}$$
 
@@
 
--   Percentage of female MoMA directors, an explanatory variable, is a numeric variable between 0 and 100 indicating the gender distribution of the directors who had the decision-making power to choose the artists to be displayed
+-   Percentage of female MoMA directors and department heads, an explanatory variable, is a numeric variable between 0 and 100 indicating the gender distribution of the directors who had the decision-making power to choose the artists to be displayed
 
 -   Year, an explanatory variable, is a numeric variable between 1929 (the founding year of the MoMA) and 2023 (the year that this report was published) indicating a specific year in the history of the MoMA
-
-All of the models are run in R [@R] and displayed using modelsummary [@modelsummary].
 
@@
 For the first two models regarding the effect of time on the percentage of female MoMA directors and on artists, time was chosen to be evaluated because there has been an increased push for gender equality in workplaces across the United States over the years.
-Because of this, a positive relationship between time in years and the percentage of female directors and female artists is expected for both the first linear regression model (regarding the effect of time on the percentage of female MoMA directors) and the second linear regression model (regarding the effect of time on the percentage of female MoMA artists).
+Because of this, a positive relationship between time in years and the percentage of female directors and female artists is expected for both the first linear regression model (regarding the effect of time on the percentage of female MoMA directors and department heads) and the second linear regression model (regarding the effect of time on the percentage of female MoMA artists).
 
-Given these two models, it is worth investigating whether there is a relationship between the percentage of female directors and the percentage of female artists, to determine whether female directors are more likely to be aware of gender inclusion and thus display more female artists than their male counterparts.
-Because women are subjects of workplace gender discrimination, they are more likely to be aware of the need for inclusive gender representation, so a positive relationship between time in years and the percentage of female directors and female artists is expected.
+Given these two models, it is worth investigating whether there is a relationship between the two: the percentage of female directors / department heads and the percentage of female artists, to determine whether female directors and department heads are more likely to be aware of gender inclusion and thus display more female artists than their male counterparts.
+Because women are often subject to workplace gender discrimination, they are more likely to be aware of the need for inclusive gender representation, so a positive relationship between time in years and the percentage of female directors and female artists is expected.
 
-# Results
-The results of the first linear regression model of the effect of time on the percentage of female MoMA directors is summarized in @tbl-modelresults1.
-The prediction of a positive relationship between time in years and the percentage of female MoMA directors proved correct, with the percentage of female directors increasing every year by 0.25 percentage points since the MoMA's founding in 1929.
+# Results {#sec-results}
+The results of the first linear regression model of the effect of time on the percentage of female MoMA directors and department heads is summarized in @tbl-modelresults1.
+The prediction of a positive relationship between time in years and the percentage of female MoMA directors / department heads proved correct, with the percentage of female directors and department heads increasing every year by 0.25 percentage points since the MoMA's founding in 1929.
 We know that this finding is significant because the p-value of this model is less than the threshold of 0.05.
@@
 #| label: tbl-modelresults1
-#| tbl-cap: "Explanatory model of percentage of female MoMA directors based on year"
+#| tbl-cap: "Explanatory model of percentage of female MoMA directors and department heads based on year"
 #| warning: false
@@
 #| label: fig-model1
-#| fig-cap: Linear model of percentage of female MoMA directors by year
+#| fig-cap: Linear model of percentage of female MoMA directors and department heads by year
 #| echo: false
@@
     x = "Time (Years)",
-    y = "Percentage of Female MoMA Directors"
-  ) 
+    y = "Percentage of Female MoMA Directors 
+    and Department heads"
+  ) + 
+  theme_minimal()
 ```
@@
 @fig-model2 demonstrates this  relationship as a scatterplot, better visualizing the positive linear relationship between the amount of women artists who have been displayed in MoMA exhibits and time.
+
+The effect of time on the percentage of female MoMA artists, 0.08 percentage points per year, is smaller than the effect of time on the percentage of female MoMA directors and department heads, 0.25 percentage points per year.
+This could partly be explained by the data for directors and department heads (65 observations) being much smaller than the data for artists (32,537 observations).
+It could also be explained by the fact that the artists data only goes up to 1990, whereas the directors and department heads data goes up to the present.
+Within the 30 years between 1990 and the present, there has been an increased awareness of gender inclusivity across society, which may have been reflected in the directors and department dataset but not in the artists dataset due to the measurement practices of the MoMA data.
 ```{r}
@@
     y = "Percentage of Female MoMA Artists"
-  ) 
+  ) + 
+  theme_minimal()
 ```
@@
 
-The results of the third linear regression model of the effect of time and the percentage of female MoMA directors on the percentage of female MoMA artists is summarized in @tbl-modelresults3.
+The results of the third linear regression model of the effect of time and the percentage of female MoMA decision-making staff on the percentage of female MoMA artists is summarized in @tbl-modelresults3.
 The prediction of a positive relationship between time in years and the percentage of female directors and the percentage of female MoMA artists proved correct, with the percentage of female artists increasing by 0.10 percentage points with every 1% increase in the percentage of female directors.
@@
 #| label: tbl-modelresults3
-#| tbl-cap: "Explanatory model of percentage of female MoMA artists based on exhibit year and percentage of female MoMA directors "
+#| tbl-cap: "Explanatory model of percentage of female MoMA artists based on exhibit year and percentage of female MoMA directors and department heads"
 #| warning: false
@@
 
-## Gender Distribution 
+## Gender Distribution in the MoMA
 From @fig-artistgender and @fig-staffgender, we see that there is a significant gap between representation of men versus women in the MoMA, both for the artists displayed and for the museum staff with the most power.
 Comparing @fig-artistgender and @fig-staffgender, the men:women ratio is more unequal in the artists, at a ratio of 10:1, than in the directors and department heads, at a ratio of 4:1.
+This may be partly explained by the nature of the data, as the dataset for MoMA artists is much larger than that of the directors / department heads and only goes up to 1990.
 
-This distribution is surprising, especially given that the MoMA was founded due to the works and ideas of women: Lillie P.
+This unequal gender distribution is surprising, especially given that the MoMA was founded in large part due to the works and ideas of women: Lillie P.
 Bliss, Mary Quinn Sullivan, and Abby Aldrich Rockefeller - three influential women who were patrons of the arts in the 1920s [@MoMA].
-One potential reason for this could be American society's historical attitude towards women versus men, tending to elevate and encourage men to pursue careers as artists or museum curators and discouraging women to.
+One potential reason for this could be American society's historical attitude towards women versus men, tending to elevate and encourage men to pursue professional careers and discouraging women to.
 Another reason could be related to the findings of the third model found in @tbl-modelresults3: if women directors and department heads are more likely to choose women artists' work to exhibit, the same may go for men directors and department heads with men artists.
@@
 
-## Nationality Distribution 
+## Nationality Distribution in the MoMA
 @fig-artistnationality and @fig-staffnationality show us that the museum is predominantly made up of American representation, both in its artists and in its decision-making staff.
@@
 This inevitably led to the results of the gender distribution analysis being biased and not entirely accurate.
+A third weakness would be the lack of data for MoMA artists after 1990, as mentioned above in #sec-results.
 
-Thus, an appropriate next step would be to conduct more research on the demographics of the artists, directors, and department heads of the MoMA so that a more accurate and meaningful analysis can be conducted.
+Thus, an appropriate next step would be to conduct more research on the demographics of the artists, directors, and department heads of the MoMA (especially of artists after 1990) so that a more accurate and meaningful analysis can be conducted.
 Not only would this account for some of the missing values that were excluded in this paper, this could result in analysis on racial equality in the MoMA.
